---
title: Bold Vision Youth Thriving Survey 
subtitle: Trends by Race and Question
author: Catalyst California in collaboration with Bold Vision
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 3
    toc_float: yes
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(RPostgreSQL)
library(sf)
library(tidyr)
library(tidyverse)
library(srvyr)
library(survey)
library(knitr)
library(kableExtra)
library(weights)
options(scipen=999)

# connect to postgres and pull credentials
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

svy_dd <- dbGetQuery(con, "SELECT * FROM youth_thriving.bvys_datadictionary_2024 where response_type = 'mc'")

df_merged_per_race <- dbGetQuery(con, "SELECT * FROM youth_thriving.response_analysis_per_race") 

df_merged_per_race <- dbGetQuery(con, "SELECT * FROM youth_thriving.response_analysis_per_race") %>%
  mutate(race_labels = if_else(race == 'latinx', 'Latine',
                              if_else(race == 'nh_aian', 'American Indian & Alaska Native',
                                      if_else(race == 'nh_black', 'Black',
                                              ifelse(race == 'nh_white', 'White',
                                                     if_else(race == 'nh_asian', 'Asian',
                                                              if_else(race == 'nh_swana', 'Southwest Asian & North African',
                                                                      if_else(race == 'nh_twoormor', 'Multiracial', 
                                                                              if_else(race == 'nh_nhpi', 'Native Hawaiian & Pacific Islander' ,'NA')))))))))
 

```
The following summarizes how youth responded to each question in the Bold Vision Youth Thriving Survey by major racial group. Questions are organized by component (e.g., Strong Minds) and subcomponent (e.g., Positive Emotions). The distribution of responses to each question for every racial group is visualized using a heatmap. The percentages shown are based on weighted estimates that adjust the Youth Thriving sample by age, sex, race, and Service Planning Area. Estimates that have a coefficient of variation greater than 40% are regarded as unstable and are suppressed from the heatmaps. 

A total of 3,444 youth ages 15-24 in Los Angeles County completed the survey.

For a corresponding analysis that shows percentages by question for all youth, see [Total Trends by Question](https://catalystcalifornia.github.io/boldvision_youththriving/Descriptive%20and%20Demographic%20Analyses/analysis_by_question).


# Strong Minds (And Bodies)

Component definition: Youth with positive mental and physical health, which includes but is not limited to positive emotions, health behaviors, cognitive development, and accessible resources that promote overall well-being for youth. Note not every aspect is measured in the Youth Thriving Survey.

## Positive Emotions

```{r, echo=FALSE}

df <- svy_dd%>%filter(response_domain=="Strong Minds" & variable_name=="Positive Emotions") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Growth Mindset

```{r, echo = FALSE}
#### NEXT CATEOGORY 
df <- svy_dd%>%filter(response_domain=="Strong Minds" & variable_name=="Growth Mindset") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Psychological Distress

```{r, echo = FALSE}
#### NEXT CATEOGORY 
df <- svy_dd%>%filter(response_domain=="Strong Minds" & variable_name=="Psychological Distress") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
time_factors<-c("None of the time","A little of the time","Some of the time","Most of the time","All of the time","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = time_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


# Positive Identity And Self-Worth

Component definition: Youth having a strong sense of self, self-worth, and hope for the future. It can include things like hope for the future, purpose, and self-efficacy.

## Self-Efficacy

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Self-Efficacy") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```


## Hope For The Future

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Hope For The Future") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


## Freedom To Explore The Self
```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Freedom To Explore The Self") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Sparks

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Sparks" & variable != 'q10b') # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
yes_factors<-c("Yes","No","Not sure","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = yes_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```



## Critical Action

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Critical Action") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```

# Caring Families And Relationships

Component definition: Relational aspects of youth thriving such as friendships, caregiver relationships, school relationships, and more to identify the caring, stable, and positive relations in a youth’s network.

## Relationships And Support

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Caring Families And Relationships" & variable_name=="Relationships/Support" & variable == 'q10a') # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
num_factors<-c("None","One","Two","Three or more","Not Sure","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = num_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Caring Families And Relationships" & variable_name=="Relationships/Support" & question_number != '10' & variable != 'q12') # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


## Connectedness 

```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Caring Families And Relationships" & variable_name=="Connectedness") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

# Cultural Identity

Component definition: The connectedness youth have to their culture/ethnic identity which includes healing practices, ethnic pride and following family traditions.

## Cultural Identity And Connection

```{r, echo=FALSE}


df <- svy_dd%>%filter(response_domain=="Cultural Identity" & variable_name=="Cultural Identity And Connection") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


# Safety

Component definition: Safety that youth feel in their neighborhoods, at school, and in their larger communities across physically safe spaces, secure relationships (not fearing bullying, violence or abandonment), and protected development (free to be children). Note not every aspect is measured in the Youth Thriving Survey.

## Personal Safety

```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Safety" & variable_name=="Personal Safety") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}


```

# Vibrant Communities

Component definition: Local resources available to youth such as open public spaces, safe spaces, accessible public transportation, and more. 

## Safe Access To Public Spaces 

```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Vibrant Communities" & variable_name=="Safe Access To Public Spaces For Social, Cultural, And Literary Opportunities") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
yes_factors_2<-c("No","Yes","Dont Know","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = yes_factors_2) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}


```

# Racial Justice, Equity, And Inclusion 

Component definition: Youth feeling comfortable, accepted, and included in all spaces they enter, regardless of race/ethnicity, gender, religion, health status, and appearance. Youth’s systemic interactions should be fair and equitable irrespective of their identity.

## Microaggressions
```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Racial Justice, Equity, And Inclusion" & variable_name=="Microaggressions") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Experiences Of Racism And Discrimination

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Racial Justice, Equity, And Inclusion" & variable_name=="Experiences Of Racism And Discrimination") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors_2<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Don't wish to answer","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors_2) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Structural Racism

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Racial Justice, Equity, And Inclusion" & variable_name=="Structural Racism") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```

```{r, include=FALSE, echo=FALSE}

dbDisconnect(con)

```