---
title: "Crosstab on LGBTQIA+ and race by psychological distress"
author: "Alicia Vo"
date: "2025-04-04"
output: html_document
---
# Get data
```{r}
library(tidyverse)
library(srvyr)
library(RPostgres)
library(ggplot2)
library(dplyr)
library(forcats)

# Get function cross_tab_df()
source("./crosstab_svyquestions.R")

# Used to connect to RDA database and RDA function for adding table comments
source("W:\\RDA Team\\R\\credentials_source.R")

# Connect to postgres
con <- connect_to_db("bold_vision")

# Pull in the survey data and data dictionary
raw_svy_data <- dbGetQuery(con, "SELECT * FROM youth_thriving.raw_survey_data")
svy_dd <- dbGetQuery(con, "SELECT * FROM youth_thriving.bvys_datadictionary_2024")

# Pull in LGBTQIA+ and race data
gender_sexuality_data <- dbGetQuery(con, "SELECT response_id, cishet_lgbtqia FROM youth_thriving.gender_sexuality_data")
race_ethnicity_data <- dbGetQuery(con, "SELECT response_id, nh_race, race_aian, race_nhpi, race_swana FROM youth_thriving.race_ethnicity_data")

# Merge SOGI and race data frames into svy_data using response_id
svy_data <- raw_svy_data %>%
  left_join(gender_sexuality_data, by = "response_id") %>%
  left_join(race_ethnicity_data, by = "response_id") 
```

# Create survey dataframe with columns needed for analyses of race by lgbtqia and psych distress
```{r}
# Clean up data to prep for crosstab of race and lgbtqia by psych distress
race_lgbtqia <- svy_data %>%
  # Select columns we need for analysis
  select(response_id, nh_race, race_nhpi, race_aian, race_swana, cishet_lgbtqia, cu, cy, weights_final) %>%
  # Filter out rows with NA values in race or lgbtqia+ identity
  filter(!nh_race %in% c("do_not_wish", "NA"), !is.na(nh_race), !is.na(cishet_lgbtqia)) 

# Check unique values of columns nh_race and cishet_lgbtqia
# qa_check <- lapply(race_lgbtqia[,c("nh_race","cishet_lgbtqia")], unique)

# Create column cy_binary and cu_binary indicating whether the respondent felt psychological distress in the past 30 days or not. A respondent who reports feeling psychological distress None of the time is labelled as 0. Otherwise, the respondent felt worthless in the past 30 days and is labelled as 1. Respondents who choose Don't wish to answer or didn't respond to the question are labelled with NA. We're combining responses for psychological distress (A little of the time, Some of the time, Most of the time, All of the time) because the sample sizes are too small otherwise.
race_lgbtqia_data <- race_lgbtqia %>%
  mutate(race_lgbtqia = paste(nh_race, ifelse(cishet_lgbtqia == 0, "& cisgender heterosexual", "& LGBTQIA+")),
         nhpi_lgbtqia = ifelse(cishet_lgbtqia == 0 & race_nhpi==1, "nhpi & cisgender heterosexual", 
                              ifelse(cishet_lgbtqia == 1 & race_nhpi==1, "nhpi & LGBTQIA+", NA)),
        aian_lgbtqia = ifelse(cishet_lgbtqia == 0 & race_aian==1, "aian & cisgender heterosexual", 
                              ifelse(cishet_lgbtqia == 1 & race_aian==1, "aian & LGBTQIA+", NA)),
         swana_lgbtqia = ifelse(cishet_lgbtqia == 0 & race_swana==1, "swana & cisgender heterosexual", 
                              ifelse(cishet_lgbtqia == 1 & race_swana==1, "swana & LGBTQIA+", NA)),
           cy_binary = case_when(is.na(cy) | cy == 6 ~ NA,
                                 cy == 1 ~ 0, 
                                 TRUE ~ 1),
           cu_binary = case_when(is.na(cu) | cu == 6 ~ NA,
                                 cu == 1 ~ 0,
                                 TRUE ~ 1))
# check recoding
table(race_lgbtqia_data$aian_lgbtqia)
table(race_lgbtqia_data$race_aian)
# same number of aian

# Counts are too low (less than 5 respondents) for nh_aian, nh_other, nh_nhpi 
raw_counts <- race_lgbtqia_data %>%
  group_by(race_lgbtqia) %>%
  summarise(count = n(), .groups = "drop")
```

## Crosstab table for race by lgbtqia+ and a REVISED binary psych distress question.
```{r}

# Get the weighted rates and unweighted counts for the crosstab
crosstab_race_lgbtqia_psych_worthless <- race_lgbtqia_data %>% as_survey_design(weights = weights_final) %>%
  group_by(race_lgbtqia, cy_binary) %>%
  summarise(count=n(), # participant records count
    rate = survey_prop(vartype=c("cv","se"),level=.90)) %>% 
  mutate(rate = rate * 100,
         rate_se = rate_se * 100,
         rate_cv=rate_cv*100) %>%  # Convert to percentages
  ungroup()%>%
  filter(!is.na(cy_binary))

# Get the weighted rates and unweighted counts for the crosstab for alone and in combination groups
crosstab_race <- function(df,racevar,var2){
  df %>% as_survey_design(weights = weights_final) %>%
    filter(!is.na(!!sym(racevar)))%>%
  group_by(!!sym(racevar), !!sym(var2)) %>%
  summarise(count=n(), # participant records count
    rate = survey_prop(vartype=c("cv","se"),level=.90)) %>% 
  mutate(rate = rate * 100,
         rate_se = rate_se * 100,
         rate_cv=rate_cv*100) %>%  # Convert to percentages
  ungroup()%>%
  filter(!is.na(!!sym(var2)))
}

crosstab_aian_lgbtqia_psych_worthless <- crosstab_race(df=race_lgbtqia_data,racevar="aian_lgbtqia",var2="cy_binary")

crosstab_nhpi_lgbtqia_psych_worthless <- crosstab_race(df=race_lgbtqia_data,racevar="nhpi_lgbtqia",var2="cy_binary")

crosstab_swana_lgbtqia_psych_worthless <- crosstab_race(df=race_lgbtqia_data,racevar="swana_lgbtqia",var2="cy_binary")

# combine all race tables
crosstab_race_lgbtqia_psych_worthless<-rbind(crosstab_race_lgbtqia_psych_worthless,
                                             crosstab_aian_lgbtqia_psych_worthless%>%rename(race_lgbtqia=aian_lgbtqia),
                                             crosstab_nhpi_lgbtqia_psych_worthless%>%rename(race_lgbtqia=nhpi_lgbtqia),
                                          crosstab_swana_lgbtqia_psych_worthless%>%rename(race_lgbtqia=swana_lgbtqia))

```

## Crosstab table for race by lgbtqia+ and ANOTHER binary psych distress question.
```{r}
# Get the weighted rates and unweighted counts for the crosstab
crosstab_race_lgbtqia_psych_hopeless <- race_lgbtqia_data %>% as_survey_design(weights = weights_final) %>%
  group_by(race_lgbtqia, cu_binary) %>%
  summarise(count=n(), # participant records count
    rate = survey_prop(vartype=c("cv","se"),level=.90)) %>% # Automatically ensures sum = 100%
  mutate(rate = rate * 100,
         rate_se = rate_se * 100,
         rate_cv=rate_cv*100) %>%  # Convert to percentages
  ungroup() %>%
  filter(!is.na(cu_binary))

# Get the weighted rates and unweighted counts for the crosstab for alone and in combination groups
crosstab_aian_lgbtqia_psych_hopeless <- crosstab_race(df=race_lgbtqia_data,racevar="aian_lgbtqia",var2="cu_binary")

crosstab_nhpi_lgbtqia_psych_hopeless <- crosstab_race(df=race_lgbtqia_data,racevar="nhpi_lgbtqia",var2="cu_binary")

crosstab_swana_lgbtqia_psych_hopeless <- crosstab_race(df=race_lgbtqia_data,racevar="swana_lgbtqia",var2="cu_binary")

# combine all race tables
crosstab_race_lgbtqia_psych_hopeless<-rbind(crosstab_race_lgbtqia_psych_hopeless,
                                             crosstab_aian_lgbtqia_psych_hopeless%>%rename(race_lgbtqia=aian_lgbtqia),
                                             crosstab_nhpi_lgbtqia_psych_hopeless%>%rename(race_lgbtqia=nhpi_lgbtqia),
                                          crosstab_swana_lgbtqia_psych_hopeless%>%rename(race_lgbtqia=swana_lgbtqia))


```

# Create survey dataframe with columns needed for analyses of lgbtqia+ by sparks and a binary  psych distress question.
```{r}
# Clean up data to prep for crosstab of race and lgbtqia by psych distress
lgbtqia_sparks <- svy_data %>%
  # Select columns we need for analysis
  select(response_id, cishet_lgbtqia, q10, cu, weights_final) %>%
  # Filter out rows with NA values and Don't wish to answer in lgbtqia+ identity and sparks
  filter(!is.na(cishet_lgbtqia), q10 %in% c(1,2,3)) 

# Check unique values of columns cishet_lgbtqia and q10
# qa_check <- lapply(lgbtqia_sparks[,c("cishet_lgbtqia","q10")], unique)

lgbtqia_sparks_data <- lgbtqia_sparks %>%
  mutate(lgbtqia_sparks = paste(
    ifelse(cishet_lgbtqia == 0, "cisgender heterosexual", " LGBTQIA+"),
    ifelse(q10 == 1, "& has a spark", 
           ifelse(q10 == 2, "& doesn't have a spark", "& not sure if has a spark"))),
    cu_binary = case_when(is.na(cu) | cu == 6 ~ NA,
                                 cu == 1 ~ 0, 
                                 TRUE ~ 1))

# Counts are sufficient
raw_counts <- lgbtqia_sparks_data %>%
  group_by(lgbtqia_sparks) %>%
  summarise(count = n(), .groups = "drop")
```

## Crosstab table for lgbtqia+ by sparks and a binary psych distress question.
```{r}
# Get the weighted rates and unweighted countsfor the crosstab
crosstab_lgbtqia_sparks_psych_hopeless <- lgbtqia_sparks_data %>% as_survey_design(weights = weights_final) %>%
  group_by(lgbtqia_sparks, cu_binary) %>%
  summarise(count=n(), # participant records count
    rate = survey_prop(vartype=c("cv","se"),level=.90)) %>% # Automatically ensures sum = 100%
  mutate(rate = rate * 100,
         rate_se = rate_se * 100,
         rate_cv=rate_cv*100) %>%  # Convert to percentages
  ungroup() %>%
  filter(!is.na(cu_binary))

```

# Plot crosstabs

## Plot for race by lgbtqia+ and a REVISED binary psych distress question.
```{r}
# Only plot groups who respond as feeling worthless in the past 30 days and order the bars in descending order
plot_data <- crosstab_race_lgbtqia_psych_worthless %>%
  filter(cy_binary == 1)

ggplot(plot_data, aes(x = race_lgbtqia, y = rate)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0("n = ", round(count,0))), hjust = -0.1, size = 3) + 
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +  # Add space on the right
  theme_minimal() +
  guides(fill = "none") +
  labs(x = NULL, y = "Rate of Feeling of Worthless in the Past 30 Days (%)")
```
## Plot for race by lgbtqia+ and ANOTHER binary psych distress question.
```{r}
# Only plot groups who respond as feeling hopeless in the past 30 days and order the bars in descending order
plot_data <- crosstab_race_lgbtqia_psych_hopeless %>%
  filter(cu_binary == 1) 

ggplot(plot_data, aes(x = race_lgbtqia, y = rate)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0("n = ", round(count,0))), hjust = -0.1, size = 3) + 
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +  # Add space on the right
  theme_minimal() +
  guides(fill = "none") +
  labs(x = NULL, y = "Rate of Feeling of Hopeless in the Past 30 Days (%)")
```

## Plot for lgbtqia+ by sparks and a binary psych distress question.
```{r}
# Only plot groups who respond as feeling hopeless in the past 30 days and order the bars in descending order
plot_data <- crosstab_lgbtqia_sparks_psych_hopeless %>%
  filter(cu_binary == 1) 

ggplot(plot_data, aes(x = lgbtqia_sparks, y = rate)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0("n = ", round(count,0))), hjust = -0.1, size = 3) + 
  coord_flip() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.2))) +  # Add space on the right
  theme_minimal() +
  guides(fill = "none") +
  labs(x = NULL, y = "Rate of Feeling of Hopeless in the Past 30 Days (%)")
```

# Add dictionary data to crosstabs
```{r}
# Join data dictionary to crosstab  

# Dictionary data for psych distress question on feelings of worthlessness
dict_var <- svy_dd %>%
  filter(variable == "cy") %>%
  select(variable, question, sub_question, response_domain, variable_name)

# Add dictionary data to crosstab
crosstab_race_lgbtqia_psych_worthless <- crosstab_race_lgbtqia_psych_worthless %>%
  mutate(dict_var)

# Dictionary data for psych distress question on feelings of hopelessness
dict_var <- svy_dd %>%
  filter(variable == "cu") %>%
  select(variable, question, sub_question, response_domain, variable_name)

# Add dictionary data to crosstabs
crosstab_race_lgbtqia_psych_hopeless <- crosstab_race_lgbtqia_psych_hopeless %>%
  mutate(dict_var)

crosstab_lgbtqia_sparks_psych_hopeless <- crosstab_lgbtqia_sparks_psych_hopeless %>%
  mutate(dict_var)
```

# Push tables to postgres

## Table crosstab_race_lgbtqia_psych_worthless
```{r}
# Write table with metadata
table_name <- "crosstab_race_lgbtqia_psych_worthless"
schema <- "youth_thriving"
indicator <- "A crosstab table for race by lgbtqia+ identity and a REVISED binary psych distress question - did the respondent feel worthless in the past 30 days at least a little of the time?"
source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Descriptive and Demographic Analyses/crosstab_LGBTQIA_race.Rmd "
qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_crosstab_LGBTQIA_race.docx"
table_comment <- paste0(indicator, source)
# dbWriteTable(con, Id(schema, table_name), crosstab_race_lgbtqia_psych_worthless, overwrite = FALSE, row.names = FALSE)

# Comment on table and columns
column_names <- colnames(crosstab_race_lgbtqia_psych_worthless) # Get column names
column_comments <- c(
  "Shows the race and gender/sexuality identity includes non-hispanic race and alone and in combo for aian, nhpi, and swana",
  "Binary variable for psychological distress question cy, did the respondent feel worthless in the past 30 days at least a little of the time?",  
  "The raw, unweighted count of the grouping (race, gender/sexuality, and feelings of worthlessnesss)",  
  "The weighted rate of the race+gender/sexuality group that experienced feelings of worthlessness (or not)",
  "CV of the rate",
  "Standard error of the rate",
  "Variable name of the psychological distress question",
  "The psychological distress survey question",
  "The psychological distress survey subquestion",
  "The component",
  "The subcomponent"
)

# add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)

```
## Table crosstab_race_lgbtqia_psych_hopeless
```{r}
# Write table with metadata
table_name <- "crosstab_race_lgbtqia_psych_hopeless"
schema <- "youth_thriving"
indicator <- "A crosstab table for race by lgbtqia+ identity and a REVISED binary psych distress question - did the respondent feel hopeless in the past 30 days at least a little of the time?"
source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Descriptive and Demographic Analyses/crosstab_LGBTQIA_race.Rmd "
qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_crosstab_LGBTQIA_race.docx"
table_comment <- paste0(indicator, source)
# dbWriteTable(con, Id(schema, table_name), crosstab_race_lgbtqia_psych_hopeless, overwrite = FALSE, row.names = FALSE)

# Comment on table and columns
column_names <- colnames(crosstab_race_lgbtqia_psych_hopeless) # Get column names
column_comments <- c(
  "Shows the race and gender/sexuality identity includes non-hispanic race and alone and in combo for aian, nhpi, and swana",
  "Binary variable for psychological distress question cu, did the respondent feel hopeless in the past 30 days at least a little of the time?",  
  "The raw, unweighted count of the grouping (race, gender/sexuality, and feelings of hopelessnesss)",  
  "The weighted rate of the race+gender/sexuality group that experienced feelings of hopelessnesss (or not)",
  "CV of the rate",
  "Standard error of the rate",
  "Variable name of the psychological distress question",
  "The psychological distress survey question",
  "The psychological distress survey subquestion",
  "The component",
  "The subcomponent"
)

# add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)

```

## Table crosstab_lgbtqia_sparks_psych_hopeless
```{r}
# Write table with metadata
table_name <- "crosstab_lgbtqia_sparks_psych_hopeless"
schema <- "youth_thriving"
indicator <- "A crosstab table lgbtqia+ identity by whether they have sparks and a REVISED binary psych distress question - did the respondent feel hopeless in the past 30 days at least a little of the time?"
source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Descriptive and Demographic Analyses/crosstab_LGBTQIA_race.Rmd "
qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_crosstab_LGBTQIA_race.docx"
table_comment <- paste0(indicator, source)
# dbWriteTable(con, Id(schema, table_name), crosstab_lgbtqia_sparks_psych_hopeless, overwrite = FALSE, row.names = FALSE)

# Comment on table and columns
column_names <- colnames(crosstab_lgbtqia_sparks_psych_hopeless) # Get column names
column_comments <- c(
  "Shows the gender/sexuality identity and whether they have sparks",
  "Binary variable for psychological distress question cu, did the respondent feel hopeless in the past 30 days at least a little of the time?",  
  "The raw, unweighted count of the grouping (gender/sexuality, whether they have sparks, and feelings of hopelessnesss)",  
  "The weighted rate of the gender/sexuality+sparks group that experienced feelings of hopelessnesss (or not)",
  "CV of the rate",
  "Standard error of the rate",
  "Variable name of the psychological distress question",
  "The psychological distress survey question",
  "The psychological distress survey subquestion",
  "The component",
  "The subcomponent"
)

# add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)

```
