---
title: Bold Vision Youth Thriving Survey 
subtitle: Analysis by Race and Questions
author: Catalyst California
date: October 2024
output:
  html_document:
    number_sections: no
    toc: yes
    toc_depth: 3
    toc_float: yes
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(data.table)
library(dplyr)
library(RPostgreSQL)
library(sf)
library(tidyr)
library(readxl)
library(tidyverse)
library(janitor)
library(srvyr)
library(survey)
library(highcharter)
library(knitr)
library(kableExtra)
library(weights)
options(scipen=999)

# connect to postgres and pull credentials
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

svy_dd <- dbGetQuery(con, "SELECT * FROM youth_thriving.bvys_datadictionary_2024 where response_type = 'mc'")

df_merged_per_race <- dbGetQuery(con, "SELECT * FROM youth_thriving.response_analysis_per_race") 

df_merged_per_race <- dbGetQuery(con, "SELECT * FROM youth_thriving.response_analysis_per_race") %>%
  mutate(race_labels = if_else(race == 'latinx', 'Latine',
                              if_else(race == 'nh_aian', 'American Indian & Alaska Native',
                                      if_else(race == 'nh_black', 'Black',
                                              ifelse(race == 'nh_white', 'White',
                                                     if_else(race == 'nh_asian', 'Asian',
                                                              if_else(race == 'nh_swana', 'Southwest Asian & North African',
                                                                      if_else(race == 'nh_twoormor', 'Multiracial', 
                                                                              if_else(race == 'nh_nhpi', 'Native Hawaiian & Pacific Islander' ,'NA')))))))))
 

```


# Strong Minds

## Positive Emotions

```{r, echo=FALSE}

df <- svy_dd%>%filter(response_domain=="Strong Minds" & variable_name=="Positive Emotions") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Growth Mindset

```{r, echo = FALSE}
#### NEXT CATEOGORY 
df <- svy_dd%>%filter(response_domain=="Strong Minds" & variable_name=="Growth Mindset") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Psychological Distress

```{r, echo = FALSE}
#### NEXT CATEOGORY 
df <- svy_dd%>%filter(response_domain=="Strong Minds" & variable_name=="Psychological Distress") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
time_factors<-c("None of the time","A little of the time","Some of the time","Most of the time","All of the time","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = time_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


# Positive Identity And Self-Worth

## Self-Efficacy

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Self-Efficacy") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```


## Hope For The Future

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Hope For The Future") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


## Freedom To Explore The Self
```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Freedom To Explore The Self") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Sparks

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Sparks" & variable != 'q10b') # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
yes_factors<-c("Yes","No","Not sure","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = yes_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```



## Critical Action

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Positive Identity And Self-Worth" & variable_name=="Critical Action") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```

# Caring Families And Relationships

## Relationships/Support

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Caring Families And Relationships" & variable_name=="Relationships/Support" & question_number != '10' & variable != 'q12') # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```



## Connectedness 

```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Caring Families And Relationships" & variable_name=="Connectedness") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

# Cultural Identity

## Cultural Identity And Connection

```{r, echo=FALSE}


df <- svy_dd%>%filter(response_domain=="Cultural Identity" & variable_name=="Cultural Identity And Connection") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
true_factors<-c("Never true","Sometimes true","Often true","Always true","Don't wish to answer") # most commonly used factor here


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = true_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```


# Safety

## Personal Safety

```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Safety" & variable_name=="Personal Safety") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}


```

# Vibrant Communities

## Safe Access To Public Spaces For Social, Cultural, And Literary Opportunities

```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Vibrant Communities" & variable_name=="Safe Access To Public Spaces For Social, Cultural, And Literary Opportunities") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
yes_factors_2<-c("No","Yes","Dont Know","Don't wish to answer")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = yes_factors_2) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}


```

# Racial Justice, Equity, And Inclusion 

## Microaggressions
```{r, echo = FALSE}
df <- svy_dd%>%filter(response_domain=="Racial Justice, Equity, And Inclusion" & variable_name=="Microaggressions") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Experiences Of Racism And Discrimination

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Racial Justice, Equity, And Inclusion" & variable_name=="Experiences Of Racism And Discrimination") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors_2<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Don't wish to answer","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors_2) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}
```

## Structural Racism

```{r, echo = FALSE}
#### NEXT CATEGORY 
df <- svy_dd%>%filter(response_domain=="Racial Justice, Equity, And Inclusion" & variable_name=="Structural Racism") # filter dictionary just for questions of interest

unique_vars <- unique(df$variable) # create a list of questions/variables to analyze

# Factor options
frequency_factors<-c("Never","Rarely","Sometimes","Most of the time","All of the time","Does not apply to me")


for (i in unique_vars) {   df<-df_merged_per_race%>%filter(variable==i)%>%filter(rate_cv<40)
my_height <- 0.95 # height and width of ggplot
my_width <- 0.95
df$response <- factor(x=df$response, levels = frequency_factors) # factor levels to order plot by
# plot styling
visual<-ggplot(data = df, aes(x = response, y = race_labels,fill=rate))+
  geom_tile(height=my_height, width=my_width, color="white",lwd = 1.5,
            linetype = 1)+
  geom_text(aes(label=round(rate,1)),size=3)+
  scale_fill_gradient(low="#f9de8d", high="#EF4A66",name="Weighted Percent")+
  scale_y_discrete(labels=function(x)str_wrap(x,width=20),)+
  scale_x_discrete(labels=function(y)str_wrap(y,width=5))+
  labs(title= str_wrap(paste0(df$question, " ", df$sub_question)), width=60,
       x="",
       y="")+
  # coord_fixed()+
  theme_bw()+
  theme(plot.title=element_text(size=10),
        legend.title=element_text(size=9),
        axis.text.x=element_text(size=10),
        axis.text.y=element_text(size=10))
print(visual)}

```

```{r, echo=FALSE}

dbDisconnect(con)

```