---
title: "Running survey demographics"
author: "Alicia Vo"
date: "2024-10-07"
output: html_document
---
## Purpose: Running survey demographics

# Pull data from database.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
library(data.table)
library(dplyr)
library(RPostgreSQL)
library(purrr)
library(stringr)
library(tibble)
library(tidyr)
library(devtools) 

# Connect to postgres
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

source("W:\\RDA Team\\R\\Github\\RDA Functions\\main\\RDA-Functions\\Utility_Functions.R")

# Pull in the raw survey data 
svy_data <- dbGetQuery(con, "SELECT * FROM youth_thriving.raw_survey_data")

# Pull in table of respondents with recoded race/ethnicity
race_ethnicity_data <- dbGetQuery(con, "SELECT * FROM youth_thriving.race_ethnicity_data")
```

# Calculate the frequencies and percentages of each race category.
```{r}
total_respondents <- nrow(svy_data)
race_demographics_df <- race_ethnicity_data %>%
  summarise(
    race_aian_count = sum(race_aian),
    race_aian_pct = round(100 * sum(race_aian) / total_responses, 1),
    
    race_black_count = sum(race_black),
    race_black_pct = round(100 * sum(race_black) / total_responses, 1),
    
    race_indigenous_count = sum(race_indigenous),
    race_indigenous_pct = round(100 * sum(race_indigenous) / total_responses, 1),
    
    race_latinx_count = sum(race_latinx),
    race_latinx_pct = round(100 * sum(race_latinx) / total_responses, 1),
    
    race_asian_count = sum(race_asian),
    race_asian_pct = round(100 * sum(race_asian) / total_responses, 1),
    
    race_nhpi_count = sum(race_nhpi),
    race_nhpi_pct = round(100 * sum(race_nhpi) / total_responses, 1),
    
    race_swana_count = sum(race_swana),
    race_swana_pct = round(100 * sum(race_swana) / total_responses, 1),
    
    race_white_count = sum(race_white),
    race_white_pct = round(100 * sum(race_white) / total_responses, 1),
    
    race_dwta_count = sum(race_dwta),
    race_dwta_pct = round(100 * sum(race_dwta) / total_responses, 1),
    
    race_other_count = sum(race_other),
    race_other_pct = round(100 * sum(race_other) / total_responses, 1))

print(race_demographics_df)
```

# Calculate the frequencies and percentages of regional Asian categories (i.e. South Asian, Southeast Asian). Percentages are based on the total count of Asian Americans being the denominator.
```{r}
total_asian <- race_demographics_df$race_asian_count

asian_regional_demographics_df <- race_ethnicity_data %>%
  summarise(
    southeast_asian_count = sum(isSoutheastAsian),
    southeast_asian_pct = round((100 * southeast_asian_count / total_asian), 1),
    south_asian_count = sum(isSouthAsian),
    south_asian_pct = round((100 * south_asian_count / total_asian), 1)
  )

print(asian_regional_demographics_df)
```

# Calculate the frequencies and percentages of detailed Asian ethnicities. Percentages are based on the total count of Asian Americans being the denominator. The sum of all percentages do not add up to 100 because some Asian ethnicities are not included (e.g. Thai, Pakistani).
```{r}
# Step 1: Create a column for the number of ethnicities listed by counting semicolons
asian_ethnicity_data <- race_ethnicity_data %>%
  filter(detailed_asian != "") %>%  # Remove any empty entries
  mutate(num_ethnicities = str_count(detailed_asian, ";") + 1) %>% # Count number of ethnicities
  select(detailed_asian, num_ethnicities)

# Step 2: Split ethnicities into separate rows but retain fractional counts
asian_ethnicity_fractions <- asian_ethnicity_data %>%
  separate_rows(detailed_asian, sep = "; ") %>%  # Split by semicolon
  group_by(detailed_asian) %>% # Group by each Asian ethnicity
  summarise(asian_ethnic_count = round(sum(1 / num_ethnicities), 1))  # Sum fractions

# Step 3: Calculate percentages
asian_ethnicity_demographics_df <- asian_ethnicity_fractions %>%
  mutate(asian_pop_pct = round(100 * asian_ethnic_count / total_asian, 1))  # Calculate percentage

# View the results
print(asian_ethnicity_demographics_df)
```

# Calculate the frequencies and percentages of detailed NHPI ethnicities. The sum of all percentages do not add up to 100 because some NHPI ethnicities are not included (e.g. Filipino).
```{r}
total_nhpi <- race_demographics_df$race_nhpi_count

# Step 1: Create a column for the number of ethnicities listed by counting semicolons
nhpi_ethnicity_data <- race_ethnicity_data %>%
  filter(detailed_nhpi != "") %>%  # Remove any empty entries
  mutate(num_ethnicities = str_count(detailed_nhpi, ";") + 1) %>% # Count number of ethnicities
  select(detailed_nhpi, num_ethnicities)

# Step 2: Split ethnicities into separate rows but retain fractional counts
nhpi_ethnicity_fractions <- nhpi_ethnicity_data %>%
  separate_rows(detailed_nhpi, sep = "; ") %>%  # Split by semicolon
  group_by(detailed_nhpi) %>% # Group by each NHPI ethnicity
  summarise(nhpi_ethnic_count = round(sum(1 / num_ethnicities), 1))  # Sum fractions

# Step 3: Calculate percentages
nhpi_ethnicity_demographics_df <- nhpi_ethnicity_fractions %>%
  mutate(nhpi_pop_pct = round(100 * nhpi_ethnic_count / total_nhpi, 1))  # Calculate percentage

# View the results
print(nhpi_ethnicity_demographics_df)
```

```{r}
# Bind the data frames into one long data frame
race_demographics <- bind_rows(
  race_demographics_df,
  asian_regional_demographics_df,
  asian_ethnicity_demographics_df,
  nhpi_ethnicity_demographics_df
)

# View the combined data frame
print(race_demographics)
```

# Calculate the frequencies and percentages of gender identities.
```{r}
# Summarise the frequency and percentage for each gender identity
gender_demographics_df <- svy_data %>%
  summarise(
    girl_woman_count = sum(fc, na.rm = TRUE),
    girl_woman_pct = round(100 * girl_woman_count / total_respondents, 1),
    
    boy_man_count = sum(fd, na.rm = TRUE),
    boy_man_pct = round(100 * boy_man_count / total_respondents, 1),
    
    trans_count = sum(fe, na.rm = TRUE),
    trans_pct = round(100 * trans_count / total_respondents, 1),
    
    genderfluid_count = sum(ff, na.rm = TRUE),
    genderfluid_pct = round(100 * genderfluid_count / total_respondents, 1),
    
    two_spirit_count = sum(fg, na.rm = TRUE),
    two_spirit_pct = round(100 * two_spirit_count / total_respondents, 1),
    
    nonbinary_genderqueer_count = sum(fh, na.rm = TRUE),
    nonbinary_genderqueer_pct = round(100 * nonbinary_genderqueer_count / total_respondents, 1),
    
    gender_questioning_count = sum(fi, na.rm = TRUE),
    gender_questioning_pct = round(100 * gender_questioning_count / total_respondents, 1),
    
    no_gender_identity_count = sum(fj, na.rm = TRUE),
    no_gender_identity_pct = round(100 * no_gender_identity_count / total_respondents, 1),
    
    gender_dont_wish_to_answer_count = sum(fk, na.rm = TRUE),
    gender_dont_wish_to_answer_pct = round(100 * gender_dont_wish_to_answer_count / total_respondents, 1),
    
    gender_something_else_count = sum(!is.na(fl) & fl != ""),  # Count non-empty "Something Else" responses
    gender_something_else_pct = round(100 * gender_something_else_count / total_respondents, 1)
  )

# View the results
print(gender_demographics_df)

```
# Calculate the frequencies and percentages of sexualities.
```{r}
sexuality_demographics_df <- svy_data %>%
  summarise(
    straight_count = sum(fo, na.rm = TRUE),
    straight_pct = round(100 * straight_count / total_respondents, 1),
    
    gay_count = sum(fp, na.rm = TRUE),
    gay_pct = round(100 * gay_count / total_respondents, 1),
    
    lesbian_count = sum(fq, na.rm = TRUE),
    lesbian_pct = round(100 * lesbian_count / total_respondents, 1),
    
    bisexual_count = sum(fr, na.rm = TRUE),
    bisexual_pct = round(100 * bisexual_count / total_respondents, 1),
    
    queer_count = sum(fs, na.rm = TRUE),
    queer_pct = round(100 * queer_count / total_respondents, 1),
    
    asexual_count = sum(ft, na.rm = TRUE),
    asexual_pct = round(100 * asexual_count / total_respondents, 1),
    
    sexuality_questioning_count = sum(fu, na.rm = TRUE),
    sexuality_questioning_pct = round(100 * sexuality_questioning_count / total_respondents, 1),
    
    sexuality_dont_know_question_count = sum(fv, na.rm = TRUE),
    sexuality_dont_know_question_pct = round(100 * sexuality_dont_know_question_count / total_respondents, 1),
    
    sexuality_dont_wish_to_answer_count = sum(fw, na.rm = TRUE),
    sexuality_dont_wish_to_answer_pct = round(100 * sexuality_dont_wish_to_answer_count / total_respondents, 1),
    
    sexuality_something_else_count = sum(!is.na(fx) & fx != ""),  # Count non-empty "Something Else" responses
    sexuality_something_else_pct = round(100 * sexuality_something_else_count / total_respondents, 1)
  )

# Step 4: View the results
print(sexuality_demographics_df)
```
```{r}
# Bind the data frames into one long data frame
gender_sexuality_demographics <- bind_rows(
  gender_demographics_df,
  sexuality_demographics_df
)

# View the combined data frame
print(gender_sexuality_demographics)
```

# Calculate frequencies and percentages for school type enrollment.
```{r}
education_demographics_df <- svy_data %>%
  summarise(
    middle_school_count = sum(ca, na.rm = TRUE),
    middle_school_pct = round(100 * middle_school_count / total_respondents, 1),
    
    high_school_count = sum(cb, na.rm = TRUE),
    high_school_pct = round(100 * high_school_count / total_respondents, 1),
    
    vocational_trade_school_count = sum(cc, na.rm = TRUE),
    vocational_trade_school_pct = round(100 * vocational_trade_school_count / total_respondents, 1),
    
    community_college_count = sum(cd, na.rm = TRUE),
    community_college_pct = round(100 * community_college_count / total_respondents, 1),
    
    four_year_college_count = sum(ce, na.rm = TRUE),
    four_year_college_pct = round(100 * four_year_college_count / total_respondents, 1),
    
    education_dont_wish_to_answer_count = sum(cf, na.rm = TRUE),
    education_dont_wish_to_answer_pct = round(100 * education_dont_wish_to_answer_count / total_respondents, 1)
  )
print(education_demographics_df)
```

# Calculate frequencies and percentages of employment status.
# DO NOT USE: the codebook has an error. instead of column bw being the "other" repsonses, column bz contains the "other" responses. this makes me unsure of what exactly the other columns are referring to. awaiting a response from the survey people.
```{r}
employment_demographics_df <- as.data.frame(NA)
# employment_demographics_df <- svy_data %>%
#   summarise(
#     full_time_employment_count = sum(bt, na.rm = TRUE),
#     full_time_employment_pct = round(100 * full_time_employment_count / total_respondents, 1),
#     
#     full_time_student_count = sum(bu, na.rm = TRUE),
#     full_time_student_pct = round(100 * full_time_student_count / total_respondents, 1),
#     
#     looking_for_work_count = sum(bv, na.rm = TRUE),
#     looking_for_work_pct = round(100 * looking_for_work_count / total_respondents, 1),
# 
#     part_time_employment_count = sum(bx, na.rm = TRUE),
#     part_time_employment_pct = round(100 * part_time_employment_count / total_respondents, 1),
#     
#     part_time_student_count = sum(by, na.rm = TRUE),
#     part_time_student_pct = round(100 * part_time_student_count / total_respondents, 1),
#     
#     dont_wish_to_answer_count = sum(bw, na.rm = TRUE),
#     dont_wish_to_answer_pct = round(100 * dont_wish_to_answer_count / total_respondents, 1),
#     
#     other_count = sum(!is.na(bz) & bz != ""),  # Count non-empty "Other" responses
#     other_pct = round(100 * other_count / total_respondents, 1)
#         
#     )
# print(employment_demographics_df)
```

```{r}
# Bind the data frames into one long data frame
education_employment_demographics <- bind_rows(
  education_demographics_df,
  employment_demographics_df # This is empty right now, awaiting response from survey people
)

# View the combined data frame
print(education_employment_demographics)
```

# Calculate the frequencies and percentages of system involvement.
# Q24. At any point have you: Lived in foster care, spent time in juvenile hall or probation camp, spent time in jail or prison, lived in a group home or residential program, or lived with relatives who were responsible for you legally? 
```{r}
# Step 1: Filter respondents who answered "Yes" (1) to Q24
system_involved_data <- svy_data %>% filter(q24 == 1)

# Step 3: Summarise the frequency and percentage for each item in Q24a
system_involved_demographics_df <- system_involved_data %>%
  summarise(
    system_involved_count = nrow(system_involved_data), # Calculate total number of system involved respondents
    system_involved_pct = round(100 * system_involved_count / total_respondents, 1),
    
    foster_care_count = sum(ga, na.rm = TRUE),
    foster_care_pct = round(100 * foster_care_count / total_respondents, 1),
    
    lived_with_relatives_count = sum(gb, na.rm = TRUE),
    lived_with_relatives_pct = round(100 * lived_with_relatives_count / total_respondents, 1),
    
    juvenile_hall_count = sum(gc, na.rm = TRUE),
    juvenile_hall_pct = round(100 * juvenile_hall_count / total_respondents, 1),
    
    group_home_count = sum(gd, na.rm = TRUE),
    group_home_pct = round(100 * group_home_count / total_respondents, 1),
    
    jail_prison_count = sum(ge, na.rm = TRUE),
    jail_prison_pct = round(100 * jail_prison_count / total_respondents, 1),
    
    system_involved_dont_wish_to_answer_count = sum(gf, na.rm = TRUE),
    system_involved_dont_wish_to_answer_pct = round(100 * system_involved_dont_wish_to_answer_count / total_respondents, 1),
    
    system_involved_other_count = sum(!is.na(gg) & gg != ""),  # Count non-empty "Other" responses
    system_involved_other_pct = round(100 * system_involved_other_count / total_respondents, 1)
  )

# Step 4: View the results
print(system_involved_demographics_df)

```
# Calculate frequencies and percentages of law enforcement involvement.
# Q25. At any point, have you ever been detained AND/OR arrested by law enforcement in any capactiy?
```{r}
arrested_demographics_df <- svy_data %>%
  summarise(
    arrested_yes_count = sum(q25 == 1, na.rm = TRUE),  # Count of "Yes" responses
    arrested_yes_pct = round(100 * arrested_yes_count / total_respondents, 1),  # Percentage of "Yes"
    
    arrested_no_count = sum(q25 == 2, na.rm = TRUE),  # Count of "No" responses
    arrested_no_pct = round(100 * arrested_no_count / total_respondents, 1),  # Percentage of "No"
    
    arrested_dont_wish_to_answer_count = sum(q25 == 3, na.rm = TRUE),  # Count of "Don't wish to answer"
    arrested_dont_wish_to_answer_pct = round(100 * arrested_dont_wish_to_answer_count / total_respondents, 1)  # Percentage of "Don't wish to answer"
  )

# View the results
print(arrested_demographics_df)
```
#Q26. At any point, have you ever been suspended, experienced an "opportunity transfer", been expelled, have been sent out of class by a teacher, had your parents contacted for a school-based incident, or arrested at school? 
```{r}
# Step 1: Calculate frequencies and percentages for Q26
school_discipline_demographics_df <- svy_data %>%
  summarise(
    school_discipline_yes_count = sum(q26 == 1, na.rm = TRUE),  # Count of "Yes" responses
    school_discipline_yes_pct = round(100 * school_discipline_yes_count / total_respondents, 1),  # Percentage of "Yes"
    
    school_discipline_no_count = sum(q26 == 2, na.rm = TRUE),  # Count of "No" responses
    school_discipline_no_pct = round(100 * school_discipline_no_count / total_respondents, 1),  # Percentage of "No"
    
    school_discipline_dont_wish_to_answer_count = sum(q26 == 3, na.rm = TRUE),  # Count of "Don't wish to answer"
    school_discipline_dont_wish_to_answer_pct = round(100 * school_discipline_dont_wish_to_answer_count / total_respondents, 1)  # Percentage of "Don't wish to answer"
  )

# View the results
print(school_discipline_demographics_df)

```

# Calculate the frequencies and percentages of immigration system involvement. 
# Q27: Do any of the following apply to you: Temporary Protected Status, Asylum Status, Refugee Status, Differed Action for Childhood Arrivals (DACA), Non-Citizen Resident?

```{r}
immigration_demographics_df <- svy_data %>%
  summarise(
    immigrant_yes_count = sum(q27 == 1, na.rm = TRUE),
    immigrant_yes_pct = round(100 * immigrant_yes_count / total_respondents, 1),
    
    immigrant_no_count = sum(q27 == 2, na.rm = TRUE),
    immigrant_no_pct = round(100 * immigrant_no_count / total_respondents, 1),
    
    immigrant_dont_know_count = sum(q27 == 3, na.rm = TRUE),
    immigrant_dont_know_pct = round(100 * immigrant_dont_know_count / total_respondents, 1),
    
    immigrant_dont_wish_to_answer_count = sum(q27 == 4, na.rm = TRUE),
    immigrant_dont_wish_to_answer_pct = round(100 * immigrant_dont_wish_to_answer_count / total_respondents, 1),
    
    immigrant_other_count = sum(q27 == 5, na.rm = TRUE),
    immigrant_other_pct = round(100 * immigrant_other_count / total_respondents, 1)
  )
print(immigration_demographics_df)
```
# Calculate the frequencies and percentages of unhoused. 
# Q28. In the past year, was there ever a time when you were homeless or had to stay in any of the following places: A shelter or emergency housing, garage, transitional housing program, motel or hotel, a car, a park, campground, another public place, trailer, motor home, temporarily in the home of a friend, family or another person?
```{r}
unhoused_demographics_df <- svy_data %>%
  summarise(
    unhoused_yes_count = sum(q28 == 1, na.rm = TRUE),
    unhoused_yes_pct = round(100 * unhoused_yes_count / total_respondents, 1),
    
    unhoused_no_count = sum(q28 == 2, na.rm = TRUE),
    unhoused_no_pct = round(100 * unhoused_no_count / total_respondents, 1),
    
    unhoused_dont_know_count = sum(q28 == 3, na.rm = TRUE),
    unhoused_dont_know_pct = round(100 * unhoused_dont_know_count / total_respondents, 1),
    
    unhoused_dont_wish_to_answer_count = sum(q28 == 4, na.rm = TRUE),
    unhoused_dont_wish_to_answer_pct = round(100 * unhoused_dont_wish_to_answer_count / total_respondents, 1)
  )
print(unhoused_demographics_df)
```


```{r}
# Bind the data frames into one long data frame
system_involvement_demographics <- bind_rows(
  system_involved_demographics_df,
  arrested_demographics_df,
  school_discipline_demographics_df,
  immigration_demographics_df,
  unhoused_demographics_df
)

# View the combined data frame
print(system_involvement_demographics)
```
# Tables are race_demographics, gender_sexuality_demographics, education_employment_demographics, system_involvement_demographics

# Export race_demographics dataframe as a table with comments
```{r}
# Write table race_demographics with metadata
schema <- "youth_thriving"
table_name <- "race_demographics"
indicator <- "Frequencies and percentages of race and ethnicity groups"
source <- "script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/getting_demographics.Rmd"
qa_filepath <- "W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_getting_demographics"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), race_demographics,
             overwrite = TRUE, row.names = FALSE)

# Add metadata for race_demographics
column_names <- colnames(race_demographics) # Get column names
column_comments <- c(
  'The columns called race_[insert race]_count give the number of respondents who identified with the specified race',
  'The columns called race_[insert race]_pct give the percentage of respondents who identified with the specified race',
  rep(NA, 18),
  'Count of Southeast Asian respondents',
  'Percentage of Southeast Asian respondents with the denominator being count of Asian American respondents',
  'Count of South Asian respondents',
  'Percentage of South Asian respondents with the denominator being count of Asian American respondents',
  'The major Asian ethnicities represented in the survey',
  'Count of each major Asian ethnicity. The count is not a whole number because we count ethnically mixed Asians as fractions of their ethnic identities',
  'Percentage of each major Asian ethnicity with the denominator being count of Asian American respondents',
  'The major NHPI ethnicities represented in the survey',
  'Count of each major NHPI ethnicity. The count is not a whole number because we count ethnically mixed NHPIs as fractions of their ethnic identities',
  'Percentage of each major NHPI ethnicity with the denominator being count of NHPI respondents')

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments) 
```
# Export gender_sexuality_demographics dataframe as a table with comments
```{r}
# Write table gender_sexuality_demographics with metadata
schema <- "youth_thriving"
table_name <- "gender_sexuality_demographics"
indicator <- "Frequencies and percentages of gender and sexuality groups"
source <- "script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/getting_demographics.Rmd"
qa_filepath <- "W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_getting_demographics"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), gender_sexuality_demographics,
             overwrite = TRUE, row.names = FALSE)

# Add metadata for gender_sexuality_demographics
column_names <- colnames(gender_sexuality_demographics) # Get column names
column_comments <- c(
  'The columns called [insert gender]_count give the number of respondents who identified with the specified gender',
  'The columns called [insert gender]_pct give the percentage of respondents who identified with the specified gender',
  rep(NA, 18),
  'The columns called [insert sexuality]_count give the number of respondents who identified with the specified sexuality',
  'The columns called [insert sexuality]_pct give the percentage of respondents who identified with the specified sexuality')

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments) 
```
# Export education_employment_demographics dataframe as a table with comments
```{r}
# Write table education_employment_demographics with metadata
schema <- "youth_thriving"
table_name <- "education_employment_demographics"
indicator <- "Frequencies and percentages of education and employment groups"
source <- "script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/getting_demographics.Rmd"
qa_filepath <- "W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_getting_demographics"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), education_employment_demographics,
             overwrite = TRUE, row.names = FALSE)

# Add metadata for education_employment_demographics
column_names <- colnames(education_employment_demographics) # Get column names
column_comments <- c(
  'The columns called [insert school type]_count give the number of respondents who attend the specified school type',
  'The columns called [insert school type]_pct give the percentage of respondents who attend the specified school type')

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments) 
```

# Export system_involvement_demographics dataframe as a table with comments
```{r}
# Write table system_involvement_demographics with metadata
schema <- "youth_thriving"
table_name <- "system_involvement_demographics"
indicator <- "Frequencies and percentages of system involved groups"
source <- "script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/getting_demographics.Rmd"
qa_filepath <- "W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_getting_demographics"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), system_involvement_demographics,
             overwrite = TRUE, row.names = FALSE)

# Add metadata for system_involvement_demographics
column_names <- colnames(system_involvement_demographics) # Get column names
column_comments <- c(
  'Count of respondents who are involved in the system, as defined by the survey',
  'Percentage of respondents who are involved in the system, as defined by the survey',
  'The columns called [insert system type]_count give the number of respondents who are involved with the specified system',
  'The columns called [insert system type]_pct give the percentage of respondents who are involved with the specified system',
  rep(NA, 12),
  'Count of respondents who have been detained or arrested',
  'Percentage of respondents who have been detained or arrested',
  'Count of respondents who have been NOT detained or arrested',
  'Percentage of respondents who have NOT been detained or arrested',
  rep(NA, 2),
  'Count of respondents who have been disciplined at school',
  'Percentage of respondents who have been disciplined at school',
  'Count of respondents who have NOT been disciplined at school',
  'Percentage of respondents who have NOT been disciplined at school',
  rep(NA, 2),
  'Count of respondents who are involved with the immigration system',
  'Percentage of respondents who are involved with the immigration system',
  'Count of respondents who are NOT involved with the immigration system',
  'Percentage of respondents who are NOT involved with the immigration system',
  rep(NA, 6),
  'Count of respondents who are unhoused',
  'Percentage of respondents who are unhoused',
  'Count of respondents who are NOT unhoused',
  'Percentage of respondents who are NOT unhoused'  
  )

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments) 
```

```{r}
dbDisconnect(con)
```

