---
title: "Grouped bar charts"
author: "Alicia Vo"
date: "2025-02-25"
output: html_document
---

#### Step 1: Loading Libraries

```{r}
library(extrafont)
library(tidyverse)
library(here)
library(dplyr)
library(data.table)
library(sf)
library(ggplot2)
library(RPostgres)
library(formattable)
library(svglite)
library(stringr)
library(tidyr)
library(showtext)
library(scales)
library(kableExtra)
library(flextable)
# library(ggchicklet)
```

#### Step 2: Setting Bold Vision Style Guide

```{r}
##Colors
gray <- "#D6D7D6"
pink <- "#F75EC1"
dark_pink <- "#EF4A66"
orange <- "#F57E20"
yellow <- "#FFBF00"
light_green <- "#00A75A"
dark_green <- "#00864A"
blue  <- "#2A12B2"
light_blue <- "#465adc"

## FONTS ## 
font_add(family = "Manifold Regular", regular = "W:/Project/OSI/Bold Vision/BV 2021/Deliverables/Bold Vision Fonts/Manifold/Fonts/manifoldcf-regular.otf")
font_add(family = "Manifold CF", regular = "W:/Project/OSI/Bold Vision/BV 2021/Deliverables/Bold Vision Fonts/Manifold/Fonts/manifoldcf-heavy.otf")
font_add(family = "HelveticaNeueLTStdMdCn", regular = "W:/Project/OSI/Bold Vision/BV 2021/Deliverables/Bold Vision Fonts/Helvetica Neue LT Std/HelveticaNeueLTStd-MdCn.otf")
font_add(family = "HelveticaNeueLTStdHvCn", regular = "W:/Project/OSI/Bold Vision/BV 2021/Deliverables/Bold Vision Fonts/Helvetica Neue LT Std/HelveticaNeueLTStd-HvCn.otf")
font_add(family = "HelveticaNeueLTStdMdCnO", regular = "W:/Project/OSI/Bold Vision/BV 2021/Deliverables/Bold Vision Fonts/Helvetica Neue LT Std/HelveticaNeueLTStd-MdCnO.otf")
font_add(family = "HelveticaNeueLTStdMd", regular = "W:/Project/OSI/Bold Vision/BV 2021/Deliverables/Bold Vision Fonts/Helvetica Neue LT Std/HelveticaNeueLTStd-Md.otf")
# font_import()
loadfonts(device = "win")
windowsFonts()
showtext_auto()
# define fonts in chart
font_title <- "HelveticaNeueLTStdHvCn"
font_subtitle <- "HelveticaNeueLTStdMdCn"
font_caption <- "Manifold Regular"
font_bar_label <- "Manifold Regular"
font_axis_label <- "Manifold Regular"
```

#### Step 3: Connect to Database and Pull Data Table of Interest

```{r}
# connect to postgres and pull credentials
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

# source the function to get crosstabs
source("W:\\Project\\OSI\\Bold Vision\\Youth Thriving Survey\\GitHub\\AV\\boldvision_youththriving\\Descriptive and Demographic Analyses\\crosstab_svyquestions.R")
```

## Function get_grouped_bar_chart()
```{r}
# To use this function, you must feed in the crosstab dataframe of the 2 relevant variables, the chart title, the 2 relevant survey questions as strings, and the data dictionary
get_grouped_bar_chart <- function(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
{
    # Filter out NA responses
    na_responses <- c("Don't wish to answer","Does not apply to me")
    crosstab_df <- crosstab_df %>%
      filter(!(response_var1 %in% na_responses | response_var2 %in% na_responses)) %>%
      mutate(rate_se=rate_se*100)
    
    # Set the chart title
    title_text <- paste(str_wrap(title_text, whitespace_only = TRUE, width = 65), collapse = "\n")

    # Set the x-axis title
    string_question_var1 <- str_wrap(string_question_var1, width = 105)
    # Reorder the x-axis labels 
    crosstab_df <- crosstab_df %>%
        mutate(response_var1 = reorder(response_var1, var1_number))
    # Wrap the x-axis labels at a reasonable width 
    x_labels <- str_wrap(unique(crosstab_df$response_var1), width = 20)
    # x_labels <- str_wrap(paste(unique(crosstab_df$response_var1),string_question_var1), width = 20)
    
    # Set the legend title
    # string_question_var2 <- str_wrap(string_question_var2, width = 15)
    # Reorder the legend labels 
    crosstab_df <- crosstab_df %>%
        mutate(response_var2 = reorder(response_var2, -var2_number))    
    # Set the bar colors
    # bar_colors <- c(dark_green,light_green,yellow,"#F26E85",dark_pink)
    bar_colors <- c("#2c7bb6","#abd9e9","#ffffbf","#fdae61","#d7191c")

    # Reverse the bar colors for the legend if needed
    var1 <- names(crosstab_df)[1]
    var2 <- names(crosstab_df)[2]
    var2_dd <- svy_dd %>%
      filter(variable==var2)
    if(length(grep("_rev$", var2_dd$likert_type))>0) {
      crosstab_df <- crosstab_df %>%
          mutate(response_var2 = reorder(response_var2, var2_number))
    }       
    
    # Set the font sizes and styles
    # chart_title_theme <- element_text(hjust = 0.0, size = 18, colour = "black", family = font_title, face = "bold")
    heading_theme <- element_text(hjust = 0.5, size = 12, colour = "black", family = font_title, face = "bold")
    # x_title_theme <- element_text(hjust = 0.0, size = 12, colour = "black", family = font_axis_label, face = "bold", margin = margin(t = 10))
    subheading_theme <- element_text(hjust = 0.5, size = 9, colour = "black", family = font_axis_label, face = "plain")
    # caption_theme <- element_text(hjust = 0.0, size = 8, colour = "black", family = font_caption, face = "plain", margin = margin(t = 10))
    
    chart_title_theme <- element_text(hjust = 0, size = 18, colour = "black", family = font_title, face = "bold", margin = margin(l = 0, b = 10))
x_title_theme <- element_text(hjust = 0.5, size = 12, colour = "black", family = font_title, face = "bold", margin = margin(t = 10, l = 0))
caption_theme <- element_text(hjust = 0, size = 8, colour = "black", family = font_caption, face = "plain", margin = margin(t = 10, l = 0))
# subheading_theme <- element_text(hjust = 0, size = 9, colour = "black", family = font_axis_label, face = "bold", margin = margin(t = 10, l = 0))

    
    # Set the caption text
    var1_q_num <- sub("^([Qq][0-9]+)\\..*", "\\1,", unique(crosstab_df$question_var1))
    var2_q_num <- sub("^([Qq][0-9]+)\\..*", "\\1,", unique(crosstab_df$question_var2))
    caption_text <- str_wrap(paste0(
      "Question: ", var1_q_num, " ",
      "Component: ", unique(crosstab_df$component_var1),
      ", Subcomponent: ", unique(crosstab_df$subcomponent_var1), ". ",
      "Question: ",var2_q_num, " ",
      "Component: ", unique(crosstab_df$component_var2),
      ", Subcomponent: ", unique(crosstab_df$subcomponent_var2), ". ",
      "Data Source: Catalyst California calculations of Bold Vision Youth Thriving Survey, 2024."
    ), width = 155)  # Apply wrapping only once

    # Plot grouped bar chart
    final_visual <- ggplot(crosstab_df, aes(fill=response_var2, y=rate, x=response_var1)) + 
      geom_bar(position="dodge", stat="identity") +          # Create bar chart 
      scale_fill_manual(values = bar_colors) +               # Set the bar colors 
      # Style legend title
      guides(fill=guide_legend(title=element_blank(),
                             # title.theme = subheading_theme, 
                             label.theme = subheading_theme)) + 
      xlab(string_question_var1) +                                # Set the x-axis title
      ylab(element_blank()) +                                           # Set the y-axis title
      labs(title = title_text, subtitle=string_question_var2, caption = caption_text) +          # Set the chart title and caption
      theme_minimal() +
      theme(
        legend.position = "top",
        legend.margin = margin(l = 0),    # Ensures no extra left margin
        axis.title.x = x_title_theme,       # Set style for x-axis title 
        axis.text.x = subheading_theme,         # Set style for x-axis labels 
        plot.caption = caption_theme,           # Set style for caption
        plot.title = chart_title_theme,         # Set style for chart title
        plot.subtitle = heading_theme,
        panel.grid.minor = element_blank(),     # Set style for grid lines
        panel.grid.major = element_blank()) +   
      # Set y-axis range and breaks  
      scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20), labels = function(x) paste0(x, "%")) +
      scale_x_discrete(labels=x_labels) 
    
    # Define base file path
    base_path <- paste0("./", 
                        unique(crosstab_df$component_var1), "/", 
                        var2, "_", var1, "_grouped_barchart")
    showtext_opts(dpi=300)
    
    # Save in SVG
    ggsave(plot = final_visual, filename = paste0(base_path, ".svg"),
       device = "svg", width = 8, height = 5.5)
    
    # Save in PNG
    # ggsave(plot = final_visual, filename = paste0(base_path, ".png"),
    #        device = "png", width = 8, height = 5.5)
    
    # Save in PDF
    # ggsave(plot = final_visual, filename = paste0(base_path, ".pdf"),
    #        device = "pdf", width = 8, height = 5.5)
    
    return(final_visual)
}
```

## Function push_crosstab_table()
```{r}
push_crosstab_table <- function(raw_crosstab, table_name){
  # Write table with metadata
  # table_name <- "crosstab_psych_distress_sparks"
  schema <- "youth_thriving"
  indicator <- paste("A crosstab table of", paste(names(raw_crosstab)[1:2], collapse = " and "))
  source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Visuals/grouped_bar_charts.Rmd "
  qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_grouped_bar_charts.docx"
  table_comment <- paste(indicator, source)
  dbWriteTable(con, 
             Id(schema = schema, table = table_name), 
             raw_crosstab)
  
  # Comment on table and columns
  column_names <- colnames(raw_crosstab) # Get column names
  column_comments <- c(
    "First survey question",
    "Second survey question",
    "Count of respondents whose responses match the first two columns in this table",
    "Standard error of the count",
    "Rate of respondents whose responses match the first two columns in this table",
    "Standard error of the rate",
    "Numeric code for the first variable",
    "Response for the first variable",
    "Main question text for the first variable",
    "Sub-question text for the first variable",
    "Component category for the first variable",
    "Subcomponent category for the first variable",
    "Numeric code for the second variable",
    "Response for the second variable",
    "Main question text for the second variable",
    "Sub-question text for the second variable",
    "Component category for the second variable",
    "Subcomponent category for the second variable")
  add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)
}
```

### Psychological Distress - Sparks
```{r}
# Get crosstab of 2 questions, Psychological Distress - Sparks 
crosstab_df <- cross_tab_df(svy_data,"q10","cy",svy_dd)

# check
# check <- crosstab_df %>%
#   group_by(q10) %>%
#   summarise(sum(rate))

title_text <- 'When youth have a "spark" in life, their mental health improves'
# string_question_var2 <- "How often during the past 30 days did you feel worthless?"
string_question_var2 <- "During the past 30 days, I felt worthless..."
string_question_var1 <- "I have a spark in my life."

get_grouped_bar_chart(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
# push_crosstab_table(crosstab_df,"crosstab_psych_distress_sparks")
```

### Psychological Distress - Microaggressions
```{r}
# Get crosstab of 2 questions, Psychological Distress - Microaggressions 
crosstab_df <- cross_tab_df(svy_data,"eo","cy",svy_dd)

# check
# check <- crosstab_df %>%
#   group_by(eo) %>%
#   summarise(sum(rate))

title_text <- "When youth experience microaggressions, their mental health suffers"

# string_question_var2 <- "How often during the past 30 days did you feel worthless?"
string_question_var2 <- "During the past 30 days, I felt worthless..."
# string_question_var1 <- "During the past 12 months, how often have you dealt with being told hurtful or offensive jokes/comments about your race?"
string_question_var1 <- "During the past 12 months, I dealt with being told hurtful or offensive jokes/comments about my race."

get_grouped_bar_chart(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
# push_crosstab_table(crosstab_df,"crosstab_psych_distress_microaggressions")
```

### Psychological Distress - Structural Racism
```{r}
# Get crosstab of 2 questions, Psychological Distress - Structural Racism  
crosstab_df <- cross_tab_df(svy_data,"et","cy",svy_dd) 

# check
# check <- crosstab_df %>%
#   group_by(et) %>%
#   summarise(sum(rate))

title_text <- "When youth lack access to quality health services, their mental health suffers"
string_question_var2 <- "During the past 30 days, I felt worthless..."
string_question_var1 <- "Poor quality health services gets in the way of me living my best life."

get_grouped_bar_chart(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
# push_crosstab_table(crosstab_df,"crosstab_psych_distress_structural_racism")
```

### Self-efficacy and hope - Caring Families And Relationships
```{r}
# Get crosstab of 2 questions, Self-efficacy and hope - Caring Families And Relationships 
crosstab_df <- cross_tab_df(svy_data,"dl","co",svy_dd) 
title_text <- "When youth have supportive relationships, they have more hope for the future"
string_question_var2 <- "I feel hopeful when I think about my future."
string_question_var1 <- "When I have a problem I have someone who will be there for me."

get_grouped_bar_chart(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
# push_crosstab_table(crosstab_df,"crosstab_self_efficacy_caring_relationships")
```

### Self-efficacy and hope - Cultural identity
```{r}
# Get crosstab of 2 questions, Self-efficacy and hope - Cultural identity   
crosstab_df <- cross_tab_df(svy_data,"dz","co",svy_dd) 
title_text <- "When youth have a positive cultural identity, they have more hope for the future"
string_question_var2 <- "I feel hopeful when I think about my future."
string_question_var1 <- "My culture helps me feel good about who I am."

get_grouped_bar_chart(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
# push_crosstab_table(crosstab_df,"crosstab_self_efficacy_cultural_identity")
```

### Self-efficacy and hope - Opportunities for community involvement/critical action
```{r}
# Get crosstab of 2 questions, Self-efficacy and hope - Opportunities for community involvement/critical action   
crosstab_df <- cross_tab_df(svy_data,"dm","co",svy_dd) 
title_text <- "When youth have opportunities for community involvement, they have more hope for the future"
string_question_var2 <- "I feel hopeful when I think about my future."
string_question_var1 <- "There are ways for me to get involved in my community."

get_grouped_bar_chart(crosstab_df,title_text,string_question_var1,string_question_var2,svy_dd)
# push_crosstab_table(crosstab_df,"crosstab_self_efficacy_community_involvement")
```
