---
title: "Calculating Nonresponse Rates for Bold Vision Youth Thriving Survey"
author: "Alicia Vo"
date: "2024-10-01"
output: html_document
---
## Purpose: Create two tables for nonresponse rates by respondent and by question.

# Pull data from database.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
library(RPostgreSQL)
library(purrr)
library(stringr)
library(tibble)

# Connect to postgres
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

# Pull in the raw survey data and data dictionary
raw_svy_data <- dbGetQuery(con, "SELECT * FROM youth_thriving.raw_survey_data")

svy_dd <- dbGetQuery(con, "SELECT * FROM youth_thriving.bvys_datadictionary_2024")

# svy_dd <- svy_dd %>%
#   mutate(response_type = if_else(variable == '10b' & response_type == 'mc', 'tf', response_type))

# Only working with x rows for quicker analysis while I'm writing the script
svy_data <- raw_svy_data # %>% head(25)
```

# Create a dataframe that matches each survey question to its corresponding variables and response type (e.g. multiple choice, true/false). Extract the questions with multiple response types.
```{r}
grouped_multiple_response_types <- svy_dd %>%
  # Get the response types for the current variables
  select(question_number, variable, response_type) %>%
  # Convert question_number to character type
  mutate(question_number = as.character(question_number)) %>%
  group_by(question_number) %>%
  # Filter response_types to keep only the questions with multiple response types. 
  filter(n_distinct(response_type) > 1) %>%
  ungroup() %>%
  # Group by question_number and response_type, and create a list of variables
  group_by(question_number, response_type) %>%
  summarize(variables = list(variable), .groups = 'drop')

grouped_multiple_response_types <- grouped_multiple_response_types %>%
  filter((question_number == '2' & response_type == "mc") |    # Keep question 2 with "mc"
         (question_number == '3' & response_type == "tf") |    # Keep question 3 with "tf"
         (question_number == '24' & response_type == "mc") |   # Keep question 24 with "mc"
         (question_number == '24' & response_type == "tf")) %>%  # Keep question 24 with "tf"
  mutate(question_number = ifelse(question_number == '24' & response_type == "tf", '24a', question_number))  
```

# Create a df that matches each survey question to its corresponding variables and response type (e.g. multiple choice, true/false). Extract the questions with single response types.
```{r}
grouped_single_response_types <- svy_dd %>%
  # Get the response types for the current variables
  select(question_number, variable, response_type) %>%
  # Convert question_number to character type
  mutate(question_number = as.character(question_number)) %>%
  group_by(question_number) %>%
  # Filter response_types to keep only the "normal" questions, aka the question_numbers with only one unique response_type. I'll have to deal with the "abnormal" questions later.
  filter(n_distinct(response_type) == 1 & !is.na(question_number)) %>%
  ungroup() %>%
  # Group by question_number and response_type, and create a list of variables
  group_by(question_number, response_type) %>%
  summarize(variables = list(variable), .groups = 'drop')

# Questions 10 and 12 involve "skip logic" and needs to be accounted for accordingly.
new_rows <- tibble(
  question_number = c('10a', '10b', '12a'),
  response_type = c('mc', 'mc', 'mc'),
  variables = list('q10a', 'q10b', 'q12a')
)

# Add new rows to grouped_single_response_types
grouped_single_response_types <- grouped_single_response_types %>%
  bind_rows(new_rows)

# Modify rows for question_number '10' and '12'
grouped_single_response_types <- grouped_single_response_types %>%
  # Filter out rows that need to be updated
  filter(!(question_number %in% c('10', '12'))) %>%

  # Add the updated rows
  bind_rows(tibble(
    question_number = c('10', '12'),
    response_type = c('mc', 'mc'),
    variables = list('q10', 'q12')
  ))


```

# Create a df that combines the survey questions with single and multiple response types.
```{r}
grouped_response_types <- bind_rows(grouped_single_response_types, grouped_multiple_response_types)
grouped_response_types <- grouped_response_types %>%
  arrange(question_number)
```

Examples of survey questions with response type 'mc' and 'tf'
---------------------------
Q8's response type is 'mc' 

Q8. How true is each of these about you?		
Never True = 1	
Sometimes True = 2
Often True = 3
Always True = 4	
Dont Wish to Answer = 5

	I have a lot to look forward to in my life	CP
	I am confident I can deal with unexpected events	CQ
	If I keep working at something, I will get better at it 	CR
	I don't give up easily	CS
---------------------------
Q7's response type is 'tf' 

Q7. I am a full-time or part-time student. Right now I am in:		
Selected = 1	Middle School	CA
Not Selected = null	High School 	CB

	Vocational or trade school	CC
	Community College or Junior College	CD
	4-year college or university 	CE
	Don't wish to answer 	CF
	
# Create dummy columns for each survey question, indicating whether the question has a response for each respondent
```{r}
# Initialize an empty data frame to store the new nonresponse columns
nonresponse_by_respondent_df <- svy_data %>% select(response_id)  # Start with a reference column, e.g., response_id

# Loop through each survey question 
for (q_num in grouped_response_types$question_number) 
{
  # Get the corresponding response type for the survey question 
  response_type <- grouped_response_types$response_type[grouped_response_types$question_number == q_num]
  
  # Extract the survey question's corresponding variables 
  variables <- unlist(grouped_response_types$variables[grouped_response_types$question_number == q_num])
  
  # These questions are unique cases
  if (q_num %in% c('4', '5', '7', '10a','10b','12a', '24a')) 
  {
    new_col_name <- paste0("nonresponse_flag_q", q_num)
    
    # Initialize the column with NA
    nonresponse_by_respondent_df[[new_col_name]] <- NA
    
    # Apply different conditions for questions with skip logic
    nonresponse_by_respondent_df[[new_col_name]] <- ifelse(
      (q_num == '4' & svy_data$av == 1) |  # The respondent is Asian, tf
      (q_num == '5' & svy_data$aw == 1) |  # The respondent is NHPI, tf
      (q_num == '7' & (svy_data$bv == 1 | svy_data$bw == 1)) | # The respondent is a full-time or part-time student, tf
      (q_num == '10a' & (svy_data$q10 == 1 | svy_data$q10 == 3 | svy_data$q10 == 4)) |  # The respondent has sparks in their life, mc
      (q_num == '10b' & svy_data$q10 == 2) |  # The respondent does not have sparks in their life, mc
      (q_num == '12a' & svy_data$q12 == 1) |  # The respondent has been in school in the past 12 months, mc
      (q_num == '24a' & svy_data$q24 == 1), # The respondent is system-involved, tf
      ifelse(rowSums(is.na(svy_data[variables])) == length(variables), 1, 0), # Summing across each question's variables, if there are as many NAs as there are variables, then it's a nonresponse. In other words, if the respondent selected any of the variable choices, then it's a response.
      NA # It's NA if the current question wasn't asked of the respondent based on the skip logic
    )
  } 
  # If the question's response type is multiple choice, we consider each variable a nonresponse if the respondent skipped any of the subquestions. Basically, it's easier to think of each subquestion as a separate question in itself.
  else if (response_type == "mc") 
  {
    # Loop through each variable in the list
    for (var in variables) 
    {
      # Create a new column name nonresponse_flag_, adjusting it based on how many subquestions the question has
      if (length(variables)==1) {new_col_name <- paste0("nonresponse_flag_q", q_num)}
      else {new_col_name <- paste0("nonresponse_flag_q", q_num, "_", var)}
      
      # Generate the new column nonresponse_flag_ without updating svy_data because I want to put the new column in a separate dataframe.
      
      # !!new_col_name unquotes the new_col_name variable, which contains the name of the new column that I'm generating dynamically (as a string). Without !!, mutate() would think I'm passing the literal name new_col_name instead of the value stored inside it.
      
      # sym() stands for symbol, and it converts a string (in this case, the variable name stored in var) into a symbol that can be evaluated in a tidyverse expression. This is necessary because mutate() expects to work with column names as symbols, not strings. The sym(var) part turns the string var (which is the name of the variable or subquestion) into a symbol so that mutate() can reference the correct column in the svy_data data frame.
      
      temp_column <- svy_data %>%
        mutate(!!new_col_name := ifelse(is.na(!!sym(var)), 1, 0)) %>%
        select(!!new_col_name)
      
      # Bind the new column to nonresponse_by_respondent_df
      nonresponse_by_respondent_df <- bind_cols(nonresponse_by_respondent_df, temp_column)
    }
  }
  # If the question's response type is true/false, we consider it a nonresponse if the respondent doesn't pick any of the offered choices (e.g. gender options)
  else if (response_type == "tf") 
  {
    # Create a new column for nonresponse_flag_q_qnum
    new_col_name <- paste0("nonresponse_flag_q", q_num)
    
    # Generate the new column without updating svy_data
    
    # Here, . is a reference to the data frame being processed at that point in the pipeline, which is svy_data. If all the variables contain NA, then it's a nonresponse.
    temp_column <- svy_data %>%
      mutate(!!new_col_name := ifelse(
        rowSums(is.na(select(., all_of(variables)))) == length(variables), 
        1, 0)) %>%
      select(!!new_col_name)
    
    # Bind the new column to nonresponse_by_respondent_df
    nonresponse_by_respondent_df <- bind_cols(nonresponse_by_respondent_df, temp_column)
  }
  # If the question's response type is open-ended, we consider it a nonresponse if there's an empty string
  else if (response_type == "oe") 
  {
    # Create a new column for nonresponse_flag_q_qnum
    new_col_name <- paste0("nonresponse_flag_q", q_num)
    
    for (var in variables) 
    {
      # Create a new column name nonresponse_flag_q_qnum
      new_col_name <- paste0("nonresponse_flag_q", q_num)
      
      # Generate the new column without updating svy_data
      temp_column <- svy_data %>%
        mutate(!!new_col_name := ifelse(sym(var)=='', 1, 0)) %>%
        select(!!new_col_name)
      
      # Bind the new column to nonresponse_by_respondent_df
      nonresponse_by_respondent_df <- bind_cols(nonresponse_by_respondent_df, temp_column)
    }
  }
}
```

# For each respondent, calculate their counts and rates of nonresponse and response 
```{r}
# Get the number of survey questions. Subtract 1 from the number of columns in order to not include response_id
nonresponse_by_respondent_df$questions_asked = rowSums(!is.na(nonresponse_by_respondent_df[-1]))
  
nonresponse_by_respondent_df <- nonresponse_by_respondent_df %>%
  mutate(
      # na.rm=TRUE skips the NA values to calculate the sums
      nonresponse_count = rowSums(select(., -response_id, -questions_asked), na.rm = TRUE), 
      nonresponse_rate = (nonresponse_count / questions_asked) * 100,
      response_count = questions_asked - nonresponse_count,
      response_rate = 100 - nonresponse_rate)  %>%
   relocate(c(questions_asked, nonresponse_count, nonresponse_rate, response_count, response_rate), .after = response_id)
```

# For each question, calculate the counts and rates of nonresponse and response
```{r}
# Calculate the nonresponse_flag_qnums' column sums and convert to data frame
nonresp_by_question <- as.data.frame(
  colSums(select(nonresponse_by_respondent_df, 
                 -response_id, -questions_asked, -nonresponse_count, 
                 -nonresponse_rate, -response_count, -response_rate), 
          na.rm = TRUE))
# Rename the 1 column to 'nonresponse_counts'
colnames(nonresp_by_question) <- "nonresponse_counts"
# Remove the prefix 'nonresponse_flag_' from the row names
rownames(nonresp_by_question) <- gsub("nonresponse_flag_", "", rownames(nonresp_by_question))

# Calculate the number of non-NA values (i.e. 0s and 1s) per question column for use as the denominator in calculating nonresponse rates for each question. Some questions have an NA value because they weren't asked of the respondent based on skip logic (i.e. q4, q5, q7, q24a).
non_na_counts <- as.data.frame(colSums(!is.na(select(nonresponse_by_respondent_df, 
                 -response_id, -questions_asked, -nonresponse_count, 
                 -nonresponse_rate, -response_count, -response_rate))))
colnames(non_na_counts) <- "non_na_counts"

# Bind non_na_counts to nonresp_by_question
nonresp_by_question <- cbind(nonresp_by_question, non_na_counts)

# Convert row names to a column named 'question' and calculate the rates
nonresp_by_question <- nonresp_by_question %>%
  rownames_to_column(var = "question") %>% # Convert row names to a column named 'question'
  mutate(
    nonresponse_rate = nonresponse_counts / non_na_counts * 100,  # Use non_na_counts as denominator
    response_count = non_na_counts - nonresponse_counts,
    response_rate = 100 - nonresponse_rate
  )

# Remove the column non_na_counts from the nonresp_by_question data frame
nonresp_by_question <- nonresp_by_question %>% select(-non_na_counts)
```

# Export nonresponse_by_respondent_df dataframe as a table with comments
```{r}
# Write table nonresp_by_respondent with metadata
table_name <- "nonresponse_by_respondent"
schema <- "youth_thriving"
indicator <- "A respondent-level table with nonresponse rates for each person, including dummy columns indicating whether each question had a response"
source <- " See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_nonresponse.docx
Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/calculating_nonresponse.Rmd"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), nonresponse_by_respondent_df,
             overwrite = TRUE, row.names = FALSE)

add_table_comments <- function(con, schema, table_name, indicator, source, column_names, column_comments) 
{
  comments <- character()
  comments <- c(comments, paste0("
    COMMENT ON TABLE ", schema, ".", table_name, " IS '", table_comment, "';"))
  for (i in seq_along(column_names)) {
    comment <- paste0("
      COMMENT ON COLUMN ", schema, ".", table_name, '."', column_names[i], '" IS \'', column_comments[i], "';
      ")
    comments <- c(comments, comment)
  }
  sql_commands <- paste(comments, collapse = "")
  dbSendQuery(con, sql_commands)
}

# Add metadata for nonresp_by_respondent
column_names <- colnames(nonresponse_by_respondent_df) # Get column names
column_comments <- c(
  'The unique ID of the respondent',
  'The number of questions the respondent was asked',
  'The count of NAs for this respondent',
  'The % of NAs for this respondent out of all the questions in the survey',
  'The count of responses for this respondent',
  'The % for this respondent out of all the questions in the survey',
  'All nonresponse_flag_question_number columns are dummy columns indicating the nonresponse (1) or response (0) of the respondent')

add_table_comments(con, schema, table_name, indicator, source, column_names, column_comments)
```

# Export nonresp_by_question dataframe as a table with comments
```{r}
# Write table nonresp_by_question with metadata
table_name <- "nonresponse_by_question"
schema <- "youth_thriving"
indicator <- "A question-level table with nonresponse rates for each question"
source <- " See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_nonresponse.docx
Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/calculating_nonresponse.Rmd"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), nonresp_by_question,
             overwrite = TRUE, row.names = FALSE)

# Add metadata for nonresp_by_question
column_names <- colnames(nonresp_by_question) # Get column names
column_comments <- c(
  'The question number',
  'The count of NAs for this question',
  'The % of NAs for this question out of all the respondents who participated in the survey and had valid, eligible responses',
  'The count of responses for this question',
  'the % of responses for this question out of all the respondents who participated the survey and had valid, eligible responses')

add_table_comments(con, schema, table_name, indicator, source, column_names, column_comments)

dbDisconnect(con)
```

```{r}

# q10b check
qa<-svy_data%>%filter(q10==2)

#100% response rate no NAs, need to update table in postgres which says 25.2% response rate
table(qa$q10b,useNA='always')

# q7check
qa<-svy_data%>%filter(bw==1 | bv==1) # need to update variables used to calculate response

vars<-svy_dd%>%filter(question_number==7)%>%select(variable)

check<-qa%>%
 select(all_of(vars$variable)) %>%  # Select all of the question domain's columns in the raw data
  mutate(across(where(is.character), ~ ifelse(!is.na(.), 1, 0))) %>% # Convert non-numeric values to 0/1
  rowwise%>%
 mutate(selected=sum(c_across(), na.rm = TRUE)) 

table(check$selected,useNA='always')
# 18 for nonresponse out of 1969 observations # doesn't check out


# q5 check
qa<-svy_data%>%filter(aw==1)

vars<-svy_dd%>%filter(question_number==5)%>%select(variable)

check<-qa%>%
 select(all_of(vars$variable)) %>%  # Select all of the question domain's columns in the raw data
  mutate(across(where(is.character), ~ ifelse(!is.na(.), 1, 0))) %>% # Convert non-numeric values to 0/1
  rowwise%>%
 mutate(selected=sum(c_across(), na.rm = TRUE)) 

table(check$selected,useNA='always')
# 6 for nonresponse out of 43 observations
6/43 # checks out

# check for other skip responses
skip_logic<-svy_dd%>%filter(notes=='only_asked_subset')

#q6
vars<-svy_dd%>%filter(question_number==6)%>%select(variable)

check<-svy_data%>%
 select(all_of(vars$variable)) %>%  # Select all of the question domain's columns in the raw data
  mutate(across(where(is.character), ~ ifelse(!is.na(.), 1, 0))) %>% # Convert non-numeric values to 0/1
  rowwise%>%
 mutate(selected=sum(c_across(), na.rm = TRUE)) 

table(check$selected,useNA='always')
# #192 out of 3444
# 192/3444
# 5.6% nonresponse # checks out

#q9 cy
table(svy_data$cy,useNA='always')
# # 1 NA
# 1/3444 # checks out but don't round in table

# check response counts by respondent
# need to adjust denominator for each respondent by question they were asked
nonresponse_by_respondent_df$questions_asked=rowSums(!is.na(nonresponse_by_respondent_df[-1]))

nonresp_by_respondent_check <- nonresponse_by_respondent_df %>%
  mutate(
      nonresponse_count = rowSums(select(., -response_id), na.rm = TRUE), # na.rm=TRUE skips the NA values to calculate the sums

      nonresponse_rate = (nonresponse_count / num_questions) * 100,
      nonresponse_rate_check=(nonresponse_count / questions_asked) * 100,
      response_count = num_questions - nonresponse_count,
      response_rate = 100 - nonresponse_rate)  %>%
   relocate(c(nonresponse_count, nonresponse_rate, nonresponse_rate_check, response_count, response_rate), .after = response_id)

```

