---
title: "Recoding Race"
author: "Alicia Vo"
date: "2024-09-20"
output: html_document
---
Pull data from database.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
library(RPostgreSQL)
library(purrr)
library(stringr)

# Connect to postgres
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

# Pull in the response_id and race/ethnicity columns from the survey data
raw_svy_data <- dbGetQuery(con, "SELECT response_id, ar, \"as\", at, au, av, aw, ax, 
                       ay, az, ba, bb, bc, bd, be, bf, bg, bh, bi, bj, bk, bl, 
                       bm, bn, bo, bp, bq, br, bs FROM 
                       youth_thriving.raw_survey_data")

# isSouthAsian is a column in the data for South Asians
# isSoutheastAsian is a column in the data for Southeast Asians
# isCambodian is a column for Cambodians
svy_data <- raw_svy_data %>%
  mutate(isSouthAsian = 0,
         isSoutheastAsian = 0,
         isCambodian = 0)

# raceColumnList contains the race/ethnicity column names 
raceColumnList <- c("ar", "as", "at", "au", "av", "aw", "ax", "ay", "az", 
                    "ba", "bb", "bc", "bd", "be", "bf", "bg", "bh", "bi", 
                    "bj", "bk", "bl", "bm", "bn", "bo", "bp", "bq", "br", 
                    "bs","isSouthAsian","isSoutheastAsian","isCambodian")

svy_dd <- dbGetQuery(con, "SELECT variable, response_1 
                     FROM youth_thriving.bvys_datadictionary_2024")

# Filter svy_dd to contain the race/ethnicity column names, alongside with 
# the string description of race/ethnicity. It's helpful to view svy_dd to
# quickly decipher the meaning of each column during QA.
svy_dd <- svy_dd  %>%
  filter(variable %in% raceColumnList) %>%
  # Temporarily add the additional race recode columns as needed to create 
  # detailed_asian/detailed_nhpi cols later in script
  add_row(variable = "isCambodian", response_1 = "Cambodian")
  

```

Clean up responses where survey skip logic failed (e.g., If respondents didn't 
identify as Asian in Q3, force the response to Q4 to be NA.; same for NHPI and Q5)
Also clean all write-in columns for race questions (ba, bh, br) and create an
_original col for QA purposes
```{r}
# Correct skip logic failures across Q3, Q4, and Q5 
svy_data_clean <- svy_data %>%
  # clean Q4 columns (Asian) to remove folks where av = NA
  mutate(across(c(bb, bc, bd, be, bf, bg, bh, bi), 
                ~ case_when(is.na(av) ~ NA,
                            !is.na(av) ~ .))) %>%
  # clean Q5 columns (NHPI) to remove folks where aw = NA
  mutate(across(c(bj, bk, bl, bm, bn, bo, bp, bq, br, bs), 
                ~ case_when(is.na(aw) ~ NA,
                            !is.na(aw) ~ .))) %>%
  mutate(ba_original = ba, 
         ba_clean = gsub("[Other race. Please write in:] ", "", ba, fixed=TRUE),
         bh_original = bh, 
         bh_clean = gsub("[Other. Please write in:] ", "", bh, fixed=TRUE),
         # for QA purposes since ba will be overwritten/corrected later in script
         br_original = br, 
         # remove common piece of write-in string to simplify regex conditions later on
         br_clean = gsub("[Other. Please write in:] ", "", br, fixed=TRUE)) %>% 
  
  mutate(ba_clean = tolower(ba_clean),
         bh_clean = tolower(bh_clean),
         # make all write-ins lowercase to help find distinct values
         br_clean = tolower(br_clean)) %>% 
  mutate(ba_clean = gsub("\\s*,\\s*",",", ba_clean),
         bh_clean = gsub("\\s*,\\s*",",", bh_clean),
         # clean white space for accurate regex conditions (e.g., ^ or $)
         br_clean = gsub("\\s*,\\s*",",", br_clean)) 

# QA check to make sure string manipulation is working
qa_clean <- svy_data_clean %>%
  select(response_id, 
         ba, ba_original, ba_clean, 
         bh, bh_original, bh_clean, 
         br, br_original, br_clean, everything())

```

Get unique responses of respondents who picked "Other", "Other Asian", and 
"Other NHPI" and provided a write-in response.
```{r}
# unique_other_race_responses <- svy_data_clean %>%
#   select(response_id, ba, ba_clean) %>%
#   filter(!is.na(ba)) %>%  # Optional: Filter out NA values if needed
#   # Get unique ba values, keeping the first corresponding response_id
#   distinct(ba, .keep_all = TRUE) %>%  
#   # Select original columns to keep
#   select(ba, ba_clean, response_id)  
# 
# file_name <- paste0("unique_other_race_responses_", Sys.Date(),".csv") %>%
#   gsub("-", "", .)
# 
# write.csv(unique_other_race_responses, file = paste0("race recode/", file_name), 
#           row.names = FALSE)
# 
# unique_other_asian_responses <- svy_data_clean %>%
#   select(response_id, bh, bh_clean) %>%
#   # Optional: Filter out NA values if needed
#   filter(!is.na(bh)) %>%  
#   # Get unique ba values, keeping the first corresponding response_id
#   distinct(bh_clean, .keep_all = TRUE) %>%  
#   # Select original columns to keep
#   select(bh, bh_clean, response_id)  
# 
# file_name <- paste0("unique_other_asian_responses_", Sys.Date(),".csv") %>%
#   gsub("-", "", .)
# 
# write.csv(unique_other_asian_responses, file = paste0("race recode/", file_name), 
#           row.names = FALSE)
# 
# unique_other_nhpi_responses <- svy_data_clean %>%
#   select(response_id, br, br_clean) %>%
#   # Optional: Filter out NA values if needed
#   filter(!is.na(br)) %>%  
#   # Get unique ba values, keeping the first corresponding response_id
#   distinct(br_clean, .keep_all = TRUE) %>%  
#   # Select original columns to keep
#   select(br, br_clean, response_id)  
# 
# file_name <- paste0("unique_other_nhpi_responses_", Sys.Date(),".csv") %>%
#   gsub("-", "", .)
# 
# write.csv(unique_other_nhpi_responses, file = paste0("race recode/", file_name), 
#           row.names = FALSE)
```

Create functions to recode race responses accordingly for Q3, Q4, and Q5
```{r}
# Define a function get_revised_response to recode the respondent's write-in 
# race(s) to racial categories already listed in the survey.
# Q3:
## AR	American Indian and Alaska Native
## AS	Black or African American
## AT	Indigenous from Mexico, Central America, or South America 
## AU	Latinx/Latino/a/Hispanic 
## AV	Asian or Asian American
## AW	Native Hawaiian and Pacific Islander 
## AX	South West Asian and North African 
## AY	White 
## AZ	Don't Wish to Answer
## BA	Other Race
# Q4:
## BB	Chinese
## BC	Asian Indian
## BD	Filipino
## BE	Korean
## BF	Vietnamese
## BG	Japanese 
## BH	Other (Asian)
## BI	Don't Wish to Answer 
# Q5:
## BJ	Samoan
## BK	Togan
## BL	Chamarron
## BM	Marshallese
## BN	Fijan
## BO	Māori
## BP	PNG
## BQ	Chuukese
## BR	Other (NHPI)
## BS	Don't Wish to Answer

get_revised_response <- function(response) {
  response <- unlist(response)
  #If the respondent didn't mark "Other race", leave the function now.
  if (anyNA(response)) return('') 
  
  # Initialize an empty vector. This represents the respondent's racial composition. 
  races <- list()  
  if (grepl("^Native American$", response, ignore.case = TRUE)) 
  {races <- append(races, list("ar", "not_ba"))}
  
  if (grepl("^i really don't know,i know i'm black and might be mixed with indigenous.$", 
            response, ignore.case = TRUE)) 
  {races <- append(races, list("ba", "as", "at"))}
  
  if (grepl("^jamaican/ native american$", response, ignore.case = TRUE)) 
  {races <- append(races, list("as", "ar", "not_ba"))}
  
  if (grepl("^black,white and filipino$", response, ignore.case = TRUE)) 
  {races <- append(races, list("as", "ay", "av", "bd", "not_ba"))}
  
  if (grepl("^afro/latina$|^black and hispanic$|^latino / black$|^puerto rican/jamaican$", 
            response, ignore.case = TRUE)) 
  {races <- append(races, list("as", "au", "not_ba"))}
  
  if (grepl("^african american,mexican indian$", response, ignore.case = TRUE)) 
  {races <- append(races, list("as", "au", "av", "bc", "isSouthAsian", "not_ba"))}

  if (grepl("^african american$|^Carabian$|^Caribbean$|^Nigerian$|^Jamaican$", response, ignore.case = TRUE))
  { # Recoding to Black, Latinx and South Asian
    races <- append(races, list("as", "not_ba"))}

  if (grepl("^chicano/mexican american$|^mexican american$|^hispanic$|^hispanic salvadoran$|^Mexican$|^Cuban$|^Puerto Rican$|^Purto Rican$|^Puertorrican$|^Bolivia$|^Nicaragua$", 
            response, ignore.case = TRUE))
  {races <- append(races, list("au", "not_ba"))}

  if (grepl("^asain$", response, ignore.case = TRUE))
  {races <- append(races, list("av", "not_ba"))}
    
  if(grepl("^filipino$", response, ignore.case=TRUE))
  {races <- append(races, list("av", "bd", "not_ba"))}
  
  if(grepl("^Indian$", response, ignore.case=TRUE)) 
  {races <- append(races, list("av", "bc", "isSouthAsian", "not_ba"))}
  
  if(grepl("^South Asian$|^Sri Lankan$", response, ignore.case=TRUE)) 
  {races <- append(races, list("av", "isSouthAsian", "not_ba", "bh"))}
  
  if(grepl("^Japanese$", response, ignore.case=TRUE)) 
  {races <- append(races, list("av", "bg", "not_ba"))}

  if (grepl("^armenian$", response, ignore.case = TRUE))
  {races <- append(races, list("ax", "not_ba"))}

  if (grepl("^mexican/russian$", response, ignore.case = TRUE))
  {races <- append(races, list("au", "ay", "not_ba"))}
  
  if (grepl("^cockasain/ asain$", response, ignore.case = TRUE))
  {races <- append(races, list("ay", "av", "not_ba"))}

  if (grepl("^mixed white$", response, ignore.case = TRUE))
  {races <- append(races, list("ay", "ba"))}

  if (grepl("^mixed$|^mixed race$|^multiracial$|^mixed/multiracial$|^Belizean$|^two or more$", 
            response, ignore.case = TRUE))
  {races <- append(races, list("ba"))}
  
  if (grepl("^null$", response, ignore.case = TRUE))
  {races <- append(races, list("not_ba"))}

  if (grepl("^belizean black$", response, ignore.case = TRUE))
  {races <- append(races, list("ba", "as"))}
  
  return(paste(races, collapse = "; "))
}


# Define a function get_revised_asian_response to recode the respondent's write-in 
# race(s) to racial categories already listed in the survey.
get_revised_asian_response <- function(response) {
  #If the respondent didn't mark "Other Asian", leave the function now.
  if (is.na(response)) return('') 
  
  # Initialize an empty vector. This represents the respondent's write-in response.
  ethnicities <- list()  
  
  if (grepl("^Cambodian/ Thai$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("isCambodian", "isSoutheastAsian", "bh"))}
  
  if (grepl("^taiwanese$|^tartarian/mongolian$|^central asian / uzbek$|^kazakh$", 
            response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("bh"))}
  
  if (grepl("^Bangladesh$|^Bangladeshi$|^Bengali$|^Pakistani$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("isSouthAsian", "bh"))}
  
  if (grepl("^Burmese$|^Indonesian$|^Laos$|^Thai$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("isSoutheastAsian", "bh"))}
  
  # We are choosing to NOT label Cambodians as "Other Asian" 
  if (grepl("^Cambodian$|^Khmer$", response, ignore.case = TRUE)) 
  {ethnicities <- append(ethnicities, c("isCambodian", "isSoutheastAsian", "not_bh"))} 
  
  if (grepl("^Cambodian Chinese$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("bb", "isCambodian", "isSoutheastAsian", "not_bh"))}
  
  if (grepl("^Chinese Indonesian$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("bb", "isSoutheastAsian", "bh"))}
  
  if (grepl("^Filipino$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("bd", "isSoutheastAsian", "not_bh"))}
  
  if (grepl("^Southwest Asian$", response, ignore.case = TRUE))
  {ethnicities <- append(ethnicities, c("ax", "not_bh", "not_av"))}
  
  return(paste(ethnicities, collapse = "; "))
  
}


# Define a function get_revised_nhpi_response to recode the respondent's write-in 
# race(s) to racial categories already listed in the survey.
get_revised_nhpi_response <- function(response) {
  #If the respondent didn't mark "Other NHPI", leave the function now.
  if (is.na(response)) return('') 
  
  # Initialize an empty vector. This represents the respondent's write-in response.
  ethnicities <- list() 
  
  if (grepl("^Filipino$", response, ignore.case = TRUE)) 
  {ethnicities <- append(ethnicities, c("aw", "bd", "isSoutheastAsian", "br"))}
  
  if (grepl("^Onieda$|^Shoshone Native American$", response, ignore.case = TRUE)) 
  {ethnicities <- append(ethnicities, c("ar", "not_br", "not_aw"))}
  
  if (grepl("^Panamanian$", response, ignore.case = TRUE)) 
  {ethnicities <- append(ethnicities, c("au", "not_br", "not_aw"))}
  
  if (grepl("^Polynesian$|^Pohnpeian$", response, ignore.case = TRUE)) 
  {ethnicities <- append(ethnicities, c("aw", "br"))}
 
  if (grepl("^K<U+2206>ÍvÖnaka$", response, ignore.case = TRUE)) 
  {ethnicities <- append(ethnicities, c("aw", "not_br"))}
  
  return(paste(ethnicities, collapse = "; "))
}

```

Recode respondents who selected "Other Race" accordingly.
```{r}
# Extract the race of respondents who marked "Other race", 
# stored in the column revised_response.
svy_data_revised <- svy_data_clean %>%
  rowwise() %>%
  mutate(
    # Extract the revised response and correct ba if needed
    revised_response = map_chr(ba_clean, get_revised_response),
    # If revised_response doesn't contain ba, the respondent actually marked 
    # "Other race" incorrectly. Therefore, unmark "Other race" in the survey data.      
    ba = case_when(
      grepl("\\bnot_ba\\b", revised_response) ~ NA,
      grepl("\\bba\\b", revised_response) ~ ba)) %>%
  ungroup() %>%
  mutate(  
    # Mark the respondent's correct race(s) based on revised_response
    across(all_of(setdiff(raceColumnList, "ba")),  
           ~ ifelse(str_detect(revised_response, paste0("\\b", cur_column(), "\\b")), 1, .))) %>%
  mutate(
    # If ba write-in is relevant to bh_/br_ write-ins then combine write-ins
    # should only be needed for bh (re: Sri Lankan, South Asian)
    bh_clean = case_when((bh==1 & is.na(bh_clean)) ~ ba_clean,
                         (bh==1 & !is.na(bh_clean)) ~ paste(bh_clean, ba_clean, sep="; "),
                         (br==1 & is.na(br_clean)) ~ ba_clean,
                   (br==1 & !is.na(br_clean)) ~ paste(br_clean, ba_clean, sep=", "),
                   .default = bh_clean))

# qa check
qa_revised_other <- svy_data_clean %>%
  select(response_id, all_of(raceColumnList)) %>%
  left_join(
    select(svy_data_revised, response_id, all_of(raceColumnList), ba_clean, revised_response), 
    by=c("response_id")) %>%
  select(order(colnames(.))) %>%
  select(response_id, revised_response, ba_clean, everything())

```

Recode respondents who selected "Other Asian" accordingly.
```{r}
# Extract the race of respondents who marked "Other Asian", 
# stored in the column revised_asian_response.
svy_data_revised_other_asian <- svy_data_revised %>%
  rowwise() %>%
  mutate(
    # Extract the revised response and correct bh if needed
    revised_asian_response = map_chr(bh_clean, get_revised_asian_response),
    # If revised_asian_response doesn't contain bh, the respondent actually marked 
    # "Other race" incorrectly. Therefore, unmark "Other race" in the survey data.      
    bh = case_when(
      grepl("\\bnot_bh\\b", revised_asian_response) ~ NA,
      grepl("\\bbh\\b", revised_asian_response) ~ bh,
      .default = bh),
    # If "Other race" marked incorrectly, replace bh_clean with NA
    bh_clean = ifelse(grepl("\\bnot_bh\\b", revised_asian_response)==TRUE, NA, bh_clean),
    av = case_when(
      grepl("\\bnot_av\\b", revised_asian_response) ~ NA,
      .default = av)) %>%
  ungroup() %>%
  mutate(  
    # Mark the respondent's correct race(s) based on revised_response
    across(all_of(setdiff(raceColumnList, "bh")),  
          ~ ifelse(str_detect(revised_asian_response, paste0("\\b", cur_column(), "\\b")), 1, .)))

# qa check
qa_revised_other_asian <- svy_data_clean %>%
  select(response_id, all_of(raceColumnList)) %>%
  left_join(select(svy_data_revised_other_asian, response_id, all_of(raceColumnList), 
                   bh_clean, revised_asian_response, isCambodian, isSouthAsian, 
                   isSoutheastAsian,), by=c("response_id")) %>%
  select(order(colnames(.))) %>%
  select(response_id, revised_asian_response, bh_clean, 
         isCambodian.x, isCambodian.y, 
         isSouthAsian.x, isSouthAsian.y, 
         isSoutheastAsian.x, isSoutheastAsian.y, 
         starts_with("b"), everything())

```

Recode respondents who selected "Other NHPI" accordingly.
```{r}

# Extract the race of respondents who marked "Other NHPI", 
# stored in the column revised_nhpi_response.
svy_data_revised_other_nhpi <- svy_data_revised_other_asian %>%
  rowwise() %>%
  mutate(
    # Extract the revised response and correct br if needed
    revised_nhpi_response = map_chr(br_clean, get_revised_nhpi_response),
    
    # If revised_nhpi_response doesn't contain br, the respondent actually marked 
    # "Other NHPI" incorrectly. Therefore, unmark br in the survey data.      
    br = case_when(
      grepl("\\bnot_br\\b", revised_nhpi_response) ~ NA,
      grepl("\\bbr\\b", revised_nhpi_response) ~ br),
    # If "Other race" marked incorrectly, replace bh_clean with NA
    br_clean = ifelse(grepl("\\bnot_br\\b", revised_nhpi_response)==TRUE, NA, br_clean),
    
    # If revised_nhpi_response contains "not_aw", the respondent actually marked 
    # "NHPI" incorrectly. Therefore, unmark "NHPI" in the survey data.
    aw  = ifelse(grepl("not_aw", revised_nhpi_response, ignore.case = TRUE), NA, aw)) %>%
  ungroup() %>%
  mutate(  
    # Mark the respondent's correct race(s) based on revised_response
    across(all_of(setdiff(raceColumnList, "br")),  
           ~ ifelse(str_detect(revised_nhpi_response, paste0("\\b", cur_column(), "\\b")), 1, .)))
 

# qa check
qa_revised_other_nhpi <- svy_data_clean %>%
  select(response_id, all_of(raceColumnList)) %>%
  left_join(select(svy_data_revised_other_nhpi, response_id, all_of(raceColumnList), 
                   br_clean, revised_nhpi_response, isCambodian, isSouthAsian, 
                   isSoutheastAsian,), by=c("response_id")) %>%
  select(order(colnames(.))) %>%
  select(response_id, revised_nhpi_response, br_clean, br.x, br.y,
         as.x, as.y,
         isCambodian.x, isCambodian.y, 
         isSouthAsian.x, isSouthAsian.y, 
         isSoutheastAsian.x, isSoutheastAsian.y, 
         starts_with("b"), everything()) 

```

Creating columns isSouthAsian and isSoutheastAsian 
```{r}
svy_data_revised_other_nhpi <- svy_data_revised_other_nhpi %>%
  # Mark respondents who identified as Vietnamese, Filipino, or Cambodian as Southeast Asian
  mutate(isSoutheastAsian = 
           case_when(
             bd == 1 ~ 1, # Filipino
             bf == 1 ~ 1, # Vietnamese
             isCambodian == 1 ~ 1, # Cambodian
             .default = isSoutheastAsian),
         # Mark respondents who identified as Asian Indian as South Asian
         isSouthAsian = 
           case_when(
             bc == 1 ~ 1, # Asian Indian,
             .default = isSouthAsian))
```


Creating columns to represent the race of each respondent. 
```{r}
# Step 1: Recode according to original survey categories 
svy_data_recode_final <- svy_data_revised_other_nhpi %>%
  mutate(
    race_aian = case_when(is.na(ar) ~ 0, ar == 1 ~ 1),
    race_black = case_when(is.na(as) ~ 0, as == 1 ~ 1),  
    race_indigenous = case_when(is.na(at) ~ 0, at == 1 ~ 1),
    race_latinx = case_when(is.na(au) ~ 0, au == 1 ~ 1),
    race_asian = case_when(is.na(av) ~ 0, av == 1 ~ 1),
    race_nhpi = case_when(is.na(aw) ~ 0, aw == 1 ~ 1),
    race_swana = case_when(is.na(ax) ~ 0, ax == 1 ~ 1),
    race_white = case_when(is.na(ay) ~ 0, ay == 1 ~ 1),
    race_dwta = case_when(is.na(az) ~ 0, az == 1 ~ 1),
    # If respondents pick "Other race", they write in a response.
    race_other = case_when(is.na(ba) ~ 0, ba != "" ~ 1),
  )

# Quick check on counts
sum(svy_data_recode_final$race_black, na.rm=TRUE) #663


# Step 2: Create nh_race column, which is "latinx" if the respondent is 
# Latinx. If respondent identified as 2 or more races, the column is "nh_twoormore." 
# If respondent identified as a single race, the column is "nh_[insert chosen race]".
svy_data_recode_final <- svy_data_recode_final %>%
  rowwise() %>%
  mutate(
    race_aian_indigenous = ifelse((race_aian==1 | race_indigenous==1), 1, 0),
    race_sum = sum(c(race_aian_indigenous, race_black, race_asian, race_nhpi, 
                     race_swana, race_white, race_other)),
    nh_race = case_when(
      race_latinx == 1 ~ 'latinx',                               # Prioritize Latinx
      race_sum > 1 ~ 'nh_twoormor',                              # If more than one race is selected
      (race_aian_indigenous == 1 & race_sum == 1) ~ 'nh_aian',   # If American Indian/Alaska Native
      (race_black == 1 & race_sum == 1) ~ 'nh_black',            # If Black/African American
      (race_asian == 1 & race_sum == 1) ~ 'nh_asian',            # If Asian
      (race_nhpi == 1 & race_sum == 1) ~ 'nh_nhpi',              # If Native Hawaiian/Pacific Islander
      (race_swana == 1 & race_sum == 1) ~ 'nh_swana',            # If SWANA (Southwest Asian/North African)
      (race_white == 1 & race_sum == 1) ~ 'nh_white',            # If White
      (race_dwta == 1) ~ 'do_not_wish',                          # If Don't want to answer
      (race_other == 1 & race_sum == 1) ~ 'nh_other',            # If Other race
      .default = "NA"                                            # Non-response
    )) %>%
  ungroup() %>%
  select(-race_sum)  # Remove the helper column if not needed

# Quick check on counts
table(svy_data_recode_final$nh_race)


# Step 3: Create acs_race column, which is "latino" if respondent is Latinx. 
# Single races are: nh_aian (includes aian and indigenous), nh_asian,
# nh_black, nh_nhpi, nh_white (includes white and swana per census methods) and 
# nh_other (includes other, don't wish to answer, and NA). 
# If respondent identified as 2 or more races, the label is "nh_twoormor."
# Note: labels should match values in youth_thriving.acs_pums_race_pop_15_24 table. 
svy_data_recode_final <- svy_data_recode_final %>%
  rowwise() %>%
  mutate(
    acs_race = case_when(
      nh_race == 'latinx' ~ 'latino',         # Rename to match population weight table in pg
      nh_race == 'nh_aian' ~ 'nh_aian',       # Already includes aian and indig.
      nh_race == 'nh_asian' ~ 'nh_asian',
      nh_race == 'nh_black' ~ 'nh_black',
      nh_race == 'nh_nhpi' ~ 'nh_pacisl',     # Match value in youth_thriving.acs_pums_race_pop_15_24 
      nh_race == 'nh_white' ~ 'nh_white',
      nh_race == 'nh_swana' ~ 'nh_white',     # Per census methods
      nh_race == 'nh_other' ~ 'nh_other',
      nh_race == 'do_not_wish' ~ 'nh_other',
      nh_race == 'NA' ~ 'nh_other',
      nh_race == 'nh_twoormor' ~ 'nh_twoormor'
    )) %>%
  ungroup()

# Quick check on counts
table(svy_data_recode_final$acs_race)

# latino     nh_aian    nh_asian    nh_black    nh_other   nh_pacisl nh_twoormor    nh_white 
#   1877          67         355         551         192          23         154         225 

# add qa check 
qa_check_black <- svy_data_clean %>%
  filter(as == 1) %>%
  select(response_id, as, 
         ba_original, ba_clean, 
         bh_original, bh_clean, 
         br_original, br_clean) %>%
  left_join(svy_data_recode_final, by=c("response_id")) %>%
  select(response_id, 
         as.x, as.y, 
         ba_original.x, ba_clean.x, 
         bh_original.x, bh_clean.x, 
         br_original.x, br_clean.x, 
         nh_race, acs_race, 
         everything())

```

Create the detailed_race column in svy_data, which lists the racial 
composition of each respondent. The column does not list the respondent's 
specific ethnic origins.
```{r}
svy_data_detailed <- svy_data_recode_final %>%
  rowwise() %>%
  mutate(detailed_race = {
    races <- c()  # Initialize an empty vector
    if (race_aian == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "ar"])
    if (race_black == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "as"])
    if (race_indigenous == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "at"])
    if (race_latinx == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "au"])
    if (race_asian == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "av"])
    if (race_nhpi == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "aw"])
    if (race_swana == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "ax"])
    if (race_white == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "ay"])
    if (race_dwta == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "az"])
    if (race_other == 1) races <- c(races, svy_dd$response_1[svy_dd$variable == "ba"])
    # Combine the non-empty races into a single string
    paste(races, collapse = "; ")}) %>%
  ungroup()

```

Create the detailed_asian column in svy_data, which lists the Asian ethnic 
composition of each Asian/Asian American respondent.
```{r}
# List doesn't include "bh" which inidicates "Other Asian" because we use 
# bh_clean later on to create detailed_asian
asianDetailedList <- c("bb", "bc", "bd", "be", "bf", "bg", "bi", "isCambodian")

svy_data_detailed_asian <- svy_data_detailed %>%
  mutate(bh = as.numeric(ifelse(!is.na(bh), 1, bh))) %>%
  rowwise() %>%
  mutate(
    matching_asian_cols = list({
      vals <- across(all_of(asianDetailedList))  
      names(vals)[!is.na(vals) & vals == 1]}),
    svydd_asian_vals = list(
      svy_dd$response_1[svy_dd$variable %in% matching_asian_cols]),
    detailed_asian = paste(svydd_asian_vals, collapse = "; ")) %>%
  ungroup()


# Clean up bh_clean in order to add other Asian ethnicities to detailed_asian
svy_data_detailed_asian <- svy_data_detailed_asian %>%
  mutate(
    # Only apply transformations if bh_clean is not NA
    bh_clean = ifelse(
      is.na(bh_clean), 
      bh_clean,  # Keep as NA if it is NA
      bh_clean %>%
        # Remove specific recoded ethnicities from bh_clean (case insensitive)
        str_remove_all(regex("cambodian|khmer|filipino|chinese", ignore_case = TRUE)) %>%
        
        # Replace / with ; and ensure consistent spacing
        str_replace_all("/", "; ") %>%
        
        # Convert entire string to lowercase first
        str_to_lower() %>%
        
        # Capitalize the first letter of each word
        str_to_title() %>%
        
        # Replace "Bangladesh" with "Bangladeshi"
        str_replace_all(regex("\\bBangladesh\\b", ignore_case = TRUE), "Bangladeshi") %>%
        
        # Replace "Laos" with "Laotian"
        str_replace_all(regex("\\bLaos\\b", ignore_case = TRUE), "Laotian") %>%
        
        # Remove leading/trailing whitespace
        str_trim(side = "both") %>%
        
        # Remove any leading semicolon with optional whitespace
        str_remove("^;\\s*") %>%
        
        # Ensure no extra space around semicolons
        str_replace_all("(\\w+)\\s*;\\s*(\\w+)", "\\1; \\2"))) %>%
    mutate(
    detailed_asian = case_when(
      # Concatenate detailed_asian and bh_clean only if both are not NA or empty
      ((!is.na(bh_clean) & bh_clean != "") & (!is.na(detailed_asian) & detailed_asian != "")) ~ paste0(detailed_asian, "; ", bh_clean),
      # Set detailed_asian to bh_clean if detailed_asian is NA or empty
      ((is.na(detailed_asian) | detailed_asian == "") & (!is.na(bh_clean) & bh_clean != "")) ~ bh_clean,
      # Otherwise (bh_clean is empty or NA), keep detailed_asian as is
      .default = detailed_asian)) %>%
  ungroup()
```

Create the detailed_nhpi column in svy_data, which lists the NHPI ethnic 
composition of each NHPI respondent.
```{r}
# List doesn't include "br" which inidicates "Other NHPI" because we use 
# br_clean later on to create detailed_nhpi
nhpiDetailedList <- c("bj", "bk", "bl", "bm", "bn", "bo", "bp", "bq", "bs")

svy_data_detailed_nhpi <- svy_data_detailed_asian %>%
  rowwise() %>%
  mutate(br = as.numeric(ifelse(!is.na(br), 1, br))) %>%
  rowwise() %>%
  mutate(
    matching_nhpi_cols = list({
      vals <- across(all_of(nhpiDetailedList))  
      names(vals)[!is.na(vals) & vals == 1]}),
    svydd_nhpi_vals = list(
      svy_dd$response_1[svy_dd$variable %in% matching_nhpi_cols]),
    detailed_nhpi = paste(svydd_nhpi_vals, collapse = "; ")) %>%
  ungroup()

# Clean up br_clean in order to add other NHPI ethnicities to detailed_nhpi
svy_data_detailed_nhpi <- svy_data_detailed_nhpi %>%
  mutate(
    # Only apply transformations if bh_clean is not NA
    br_clean = ifelse(is.na(br_clean), br_clean,  # Keep as NA if it is NA
      br_clean %>%
        # Replace / with ; and ensure consistent spacing
        str_replace_all("/", "; ") %>%
        
        # Convert entire string to lowercase first
        str_to_lower() %>%
        
        # Capitalize the first letter of each word
        str_to_title() %>%
        
        # Remove leading/trailing whitespace
        str_trim(side = "both") %>%
        
        # Remove any leading semicolon with optional whitespace
        str_remove("^;\\s*") %>%
        
        # Ensure no extra space around semicolons
        str_replace_all("(\\w+)\\s*;\\s*(\\w+)", "\\1; \\2"))) %>%
  mutate(
    detailed_nhpi = case_when(
      # Concatenate detailed_nhpi and br_clean only if both are not NA or empty
      ((!is.na(br_clean) & br_clean != "") & (!is.na(detailed_nhpi) & detailed_nhpi != "")) ~ paste0(detailed_nhpi, "; ", br_clean),
      # Set detailed_nhpi to br_clean if detailed_nhpi is NA or empty
      ((is.na(detailed_nhpi) | detailed_nhpi == "") & (!is.na(br_clean) & br_clean != "")) ~ br_clean,
      # Otherwise (br_clean is empty or NA), keep detailed_nhpi as is
      .default = detailed_nhpi)) %>%
  ungroup()

# Replace empty cells with NA for specified columns
svy_data_detailed_nhpi <- svy_data_detailed_nhpi %>%
  mutate(across(c(detailed_race, detailed_asian, detailed_nhpi), ~ ifelse(. == "", NA, .)))
```

One last QA check
```{r}
qa <- svy_data_detailed_nhpi %>%
  select(response_id,
         "ar", "as", "at", "au", "av", "aw", "ax", "ay", "az", "ba", 
         ba_original, ba_clean, revised_response, detailed_race,
         "bb", "bc", "bd", "be", "bf", "bg", "bh", "bi",
         "isSouthAsian","isSoutheastAsian","isCambodian",
         bh_original, bh_clean, revised_asian_response,
         matching_asian_cols, detailed_asian,
         "bj", "bk", "bl", "bm", "bn", "bo", "bp", "bq", "br", "bs", 
         br_original, br_clean, revised_nhpi_response, matching_nhpi_cols, detailed_nhpi)


svy_data_final <- svy_data_detailed_nhpi 
```

Export final data frame as relational table.
```{r}
# Get relevant columns from svy_data to put into a table in the database
final_df <- svy_data_final %>%

  select(response_id, all_of(raceColumnList),
         nh_race, acs_race, race_aian_indigenous, race_aian, 
         race_black, race_indigenous, race_latinx, race_asian, race_nhpi, 
         race_swana, race_white, race_dwta, race_other, detailed_race,
         detailed_asian, detailed_nhpi, ba_original, ba_clean, bh_original, 
         bh_clean, br_original, br_clean)

# Write table with metadata
table_name <- "race_ethnicity_data"
schema <- "youth_thriving"
indicator <- "A person-level table specifying the race and ethnicity of each respondent "
source <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_race_ethnicity_data.docx
Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/R/recoding_race.Rmd"
table_comment <- paste0("Last updated: ", Sys.Date(), ". ", indicator, source)
dbWriteTable(con, c(schema, table_name), final_df,
             overwrite = TRUE, row.names = FALSE)
# Comment on table and columns
column_names <- colnames(final_df) # Get column names
column_comments <- c(
  "A unique, numeric ID for each respondent",
  "1 flags respondents that selected or were recoded as American Indian and Alaska Native",
  "1 flags respondents that selected or were recoded as Black or African American",
  "1 flags respondents that selected or were recoded as Indigenous from Mexico, Central America, or South America",
  "1 flags respondents that selected or were recoded as Latinx/Latino/a/Hispanic",
  "1 flags respondents that selected or were recoded as Asian or Asian American",
  "1 flags respondents that selected or were recoded as Native Hawaiian and Pacific Islander",
  "1 flags respondents that selected or were recoded as South West Asian and North African",
  "1 flags respondents that selected or were recoded as White",
  "1 flags respondents that selected or were recoded as Do Not Wish to Answer",
  "1 flags respondents that selected or were recoded as Other Race",
  "1 flags respondents that selected or were recoded as Chinese",
  "1 flags respondents that selected or were recoded as Asian Indian",
  "1 flags respondents that selected or were recoded as Filipino",
  "1 flags respondents that selected or were recoded as Korean",
  "1 flags respondents that selected or were recoded as Vietnamese",
  "1 flags respondents that selected or were recoded as Japanese",
  "1 flags respondents that selected or were recoded as Other (Asian identity)",
  "1 flags respondents that selected or were recoded as Do Not Wish to Answer (Asian identity)",
  "1 flags respondents that selected or were recoded as Samoan",
  "1 flags respondents that selected or were recoded as Togan",
  "1 flags respondents that selected or were recoded as Chamarron",
  "1 flags respondents that selected or were recoded as Marshallese",
  "1 flags respondents that selected or were recoded as Fijan",
  "1 flags respondents that selected or were recoded as Maori",
  "1 flags respondents that selected or were recoded as PNG",
  "1 flags respondents that selected or were recoded as Chuukese",
  "1 flags respondents that selected or were recoded as Other (NHPI identity)",
  "1 flags respondents that selected or were recoded as Do Not Wish to Answer (NHPI identity)",
  "0/1 flag for whether the respondent is South Asian (CC-Added Asian identity; incl. Bangladeshi, Bengali, Indian, Pakistani, and Sri Lankan)",
  "0/1 flag for whether the respondent is Southeast Asian (CC-Added Asian identity; incl. Burmese, Cambodian, Filipino, Indonesian, Khmer, Laotian, Thai, and Vietnamese)",  
  "0/1 flag for whether the respondent is Cambodian (CC-Added Asian identity, not included in Other (Asian identity))",
  "A string for whether the respondent is latinx, nh_twoormor, nh_aian_indigenous, nh_asian, nh_nhpi, nh_swana, nh_white, do_not_wish, nh_other",
  "A string that uses acs race labels: latino, nh_aian (incl. indigenous), nh_asian, nh_black, nh_other (incl. do not wish, NA, other), nh_pacisl (nh_nhpi), nh_twoormor, nh_white (incl. nh_swana)",
  "0/1 flag for whether the respondent is AIAN or indigenous from Mexico, Central America, or South America",
  "0/1 flag for whether the respondent is American Indian or Alaskan Native",
  "0/1 flag for whether the respondent is Black",
  "0/1 flag for whether the respondent is indigenous from Mexico, Central America, or South America",
  "0/1 flag for whether the respondent is Latinx/Latino/a/Hispanic",
  "0/1 flag for whether the respondent is Asian or Asian American",
  "0/1 flag for whether the respondent is Native Hawaiian and Pacific Islander",
  "0/1 flag for whether the respondent is South West Asian and North African",
  "0/1 flag for whether the respondent is White",
  "0/1 flag for whether the respondent did not wish to answer what their race is",
  "0/1 flag for whether the respondent is of another race not previously mentioned",
  "A string that lists the racial composition of each respondent. The column does not list the specific ethnic origins of each respondent",
  "A string that lists the Asian ethnic composition of each Asian/Asian American respondent",
  "A string that lists the NHPI ethnic composition of each NHPI respondent",
  
  "0/1 flag for whether the respondent is South Asian",
  "0/1 flag for whether the respondent is Southeast Asian"  
)


add_table_comments(con, schema, table_name, indicator, source, column_names, column_comments)

#dbDisconnect(con)
```