---
title: "Bold Vision Research"
# author: "Alicia Vo"
# date: "2024-12-2"
output: html_document
---

# Step 0: Data Preparation
Run these code chunks before running any subsequent steps in the research analysis (e.g. run step 0 before running step 2, no need to run step 1 to run step 2)
```{r, include=FALSE, echo=FALSE}
# Pull in data from postgres database
library(tidyverse)
library(RPostgreSQL)
library(lavaan)
library(psych)
library(kableExtra)

# Connect to postgres
source("W:\\RDA Team\\R\\credentials_source.R")
con <- connect_to_db("bold_vision")

source("W:\\RDA Team\\R\\Github\\RDA Functions\\main\\RDA-Functions\\Utility_Functions.R")

# Pull in the survey data and data dictionary
svy_data <- dbGetQuery(con, "SELECT * FROM youth_thriving.raw_survey_data")
svy_dd <- dbGetQuery(con, "SELECT * FROM youth_thriving.bvys_datadictionary_2024")
```

```{r, include=FALSE, echo=FALSE}
# Filter svy_dd and svy_data to only contain the likert questions needed for the factor analysis

# In the data dictionary, variable_name = subcomponent and response_domain = component
subcomponent_list <- c("Positive Emotions", "Self-Efficacy", "Hope For The Future", "Growth Mindset", "Psychological Distress", "Sparks", "Relationships/Support", "Freedom To Explore The Self", "Connectedness", "Critical Action", "Safe Access To Public Spaces For Social, Cultural, And Literary Opportunities", "Cultural Identity And Connection", "Experiences Of Racism And Discrimination", "Microaggressions", "Structural Racism", "Personal Safety")

component_list <- c("Strong Minds", "Positive Identity And Self-Worth", "Caring Families And Relationships", "Vibrant Communities", "Cultural Identity", "Racial Justice, Equity, And Inclusion", "Safety")

# small_svy_dd only contains the likert questions needed for the factor analysis
small_svy_dd <- svy_dd %>%
  filter(response_domain %in% component_list & !(is.na(likert_type)))

# small_svy_data only contains the columns of likert questions needed for the factor analysis
small_svy_data <- svy_data %>%
  select(all_of(small_svy_dd$variable))
```

```{r, include=FALSE, echo=FALSE}
# In the survey data, change the responses of "Don't wish to answer", "Not sure", "Not Sure",
# "Does not apply to me", "Don't know" into NA values.

na_responses <- c("Don't wish to answer", "Not sure", "Not Sure", "Does not apply to me", "Don't know")

# Iterate over each column in small_svy_data
for (col in names(small_svy_data)) {
  # Get the corresponding row in the data dictionary
  dd_row <- small_svy_dd[small_svy_dd$variable == col, ]
  
  if (nrow(dd_row) > 0) { # Ensure there is a matching dictionary entry
    # Get response_# columns
    valid_responses <- dd_row[1, grepl("^response_[0-9]+$", names(dd_row))]
    valid_responses <- valid_responses[!is.na(valid_responses)]  # Exclude NAs explicitly
    # Create response_map only if valid responses exist
    if (length(valid_responses) > 0) {
      response_map <- setNames(as.list(valid_responses), seq_along(valid_responses))
      # Replace values in the column based on the response map
      #small_svy_data[[col]] <- sapply(small_svy_data[[col]], function(x) {
      small_svy_data[[col]] <- unlist(lapply(small_svy_data[[col]], function(x) {
        if (!is.na(x) && response_map[[as.character(x)]] %in% na_responses) {
          NA
        } else {
          x
        }
      }))
    }
  }
}
```

```{r, include=FALSE, echo=FALSE}
# Reverse the likert scales in the survey data for the scales that need reversing

# Identify columns to reverse
columns_to_reverse <- small_svy_dd$variable[grep("_rev$", small_svy_dd$likert_type)]

# q10 is a special case of scale reversal; swap values 1 and 2
columns_to_reverse <- columns_to_reverse[columns_to_reverse != "q10"]
small_svy_data$q10 <- ifelse(
  is.na(small_svy_data$q10), 
  NA, 
  ifelse(small_svy_data$q10 == 1, 2, 
         ifelse(small_svy_data$q10 == 2, 1, small_svy_data$q10))
)

# Loop through each column to reverse
for (col in columns_to_reverse) {
  # Get the maximum scale value from the 'likert' column
  scale_max <- as.numeric(sub("pt_scale", "", small_svy_dd$likert[small_svy_dd$variable == col]))
  # Reverse the scale in small_svy_data
  small_svy_data[[col]] <- ifelse(is.na(small_svy_data[[col]]),
                                NA,
                                scale_max + 1 - small_svy_data[[col]])
}
```

```{r, include=FALSE, echo=FALSE}
## Data Checks

# Check that missing data is being eliminated from analysis (not adding zeros into analyses)

# Check for “wild codes” or data values outside of the allowed range

# Check that the responses of "Don't wish to answer", "Not sure", "Not Sure",

# "Does not apply to me", "Don't know" are NA values

# # Step 1: Get unique counts for small_svy_data
# unique_counts <- sapply(small_svy_data, function(x) length(unique(x)))
# 
# # Step 2: Filter relevant response columns dynamically
# # Identify columns in small_svy_dd that match the pattern "response_<number>"
# response_cols <- grep("^response_[0-9]+$", names(small_svy_dd), value = TRUE)
# 
# # Step 3: Match small_svy_data columns with small_svy_dd using the variable column
# comparison <- merge(
#   data.frame(variable = names(unique_counts), unique_count = unique_counts),
#   small_svy_dd,
#   by = "variable"
# )
# 
# # Print
# for (i in 1:nrow(comparison)) {
#   column_name <- comparison$variable[i]
#   actual_unique_values <- unique(small_svy_data[[column_name]])
# 
#   # Replace NA with a string "NA" for printing
#   actual_unique_values <- ifelse(is.na(actual_unique_values), "NA", actual_unique_values)
# 
#   cat(
#     "Column:", column_name,
#     "\nUnique Values Count:", comparison$unique_count[i],
#     "\nUnique Values:", paste(sort(actual_unique_values), collapse = ", "),
#     "\n\n"
#   )
# }
```

```{r, include=FALSE, echo=FALSE}
# Create a function for the entire process of confirmatory factor analysis (CFA),
# including the model fit measures (only ran if the model is determined to be a good fit).

run_cfa <- function(model_name) {
  # If the model is determined to be a good fit, then obtain the factor loadings. 
  # AV 12/6/24: The if statement is commented out for now, in order to see the factor loading scores regardless of the results of the model fit measures
  
 #if(run_model_fit_measures(model_name)==TRUE) {
  
    # Fit the data to a CFA model
    fit.cat <- cfa(model_name, data=small_svy_data, std.lv = TRUE,
               ordered = TRUE)
    # Define threshold for factor loadings
    threshold_factor_loading <- 0.6
    
    # Extract factor loadings and filter by threshold
    loadings_summary <- parameterEstimates(fit.cat, standardized = TRUE) %>% 
      filter(op == "=~") %>% 
      select(variable = rhs, factor_loading = est, ci.lower, ci.upper, se, p_value = pvalue) %>%
      mutate(met_threshold = abs(factor_loading) >= threshold_factor_loading) %>%
      arrange(desc(factor_loading)) # Reorder by factor_loading score in descending order
          
    # Count how many loadings met the threshold
    count_met_threshold <- loadings_summary %>%
      filter(met_threshold) %>%
      nrow()
    
    # Extract the part before the =~
    short_model_name <- sub(" =~.*", "", model_name)
    
    # Print results
    cat(short_model_name, "\n", "Number of factor loadings meeting the threshold 
        (>=", threshold_factor_loading, "):", count_met_threshold, 
        "out of", ... = nrow(loadings_summary), "items", "\n")
    print(loadings_summary)
    cat("\n")
    
    # Select specific columns from small_svy_dd for the merge
    small_svy_dd_selected <- small_svy_dd %>%
    select(variable, question, sub_question, question_number,response_domain,variable_name)
    
    # Run model fit measures if the model uses 3 or more questions 
    if(nrow(loadings_summary)<3)
    {
      fit_measures_df <- data.frame(cfi = NA, tli = NA, rmsea = NA, srmr = NA)
    }
    else
    {
      fit_measures <- fitMeasures(fit.cat,c("cfi","tli","rmsea","srmr"))
      # Convert fit_measures into a data frame
      fit_measures_df <- as.data.frame(t(as.matrix(fit_measures)))
    }
    
    # Create a dataframe with the summary results
    results_df <- loadings_summary %>%
    mutate(model_name = short_model_name,
           count_met_threshold = count_met_threshold,
           total_vars = nrow(loadings_summary)) %>%
    bind_cols(fit_measures_df) %>%
    left_join(small_svy_dd_selected, by = c("variable")) %>% 
    relocate(model_name, question, sub_question, factor_loading, met_threshold) 

    # Return the dataframe
    return(results_df)
 # }
}
```

# Step 1: Factor Analysis 
<p>Complete a confirmatory factor analysis to identify which items significantly load onto each of the youth thriving subcomponents and components. This will help us identify which items to proceed with in our analysis and identify when we may need to adjust components.</p>
```{r, include=FALSE, echo=FALSE}
# # Create the string names for the subcomponent and component CFA models based on the data dictionary

# # Group variables by subcomponents and components
# subcomponents <- small_svy_dd %>%
#   group_by(variable_name) %>%
#   summarize(variables = paste(variable, collapse = " + "), .groups = "drop")
# 
# components <- small_svy_dd %>%
#   group_by(response_domain) %>%
#   summarize(variables = paste(variable, collapse = " + "), .groups = "drop")
# 
# # Create model strings for subcomponents
# subcomponent_models <- subcomponents %>%
#   mutate(model_string = paste0(
#     "subcomponent_",
#     gsub("-", "_", gsub(",", "", gsub("/", "_", tolower(gsub(" ", "_", variable_name))))),
#     "_model <- 'subcomponent_",
#     gsub("-", "_", gsub(",", "", tolower(gsub("/", "_", gsub(" ", "_", variable_name))))),
#     " =~ ",
#     variables, "'"))
# 
# # Create model strings for components
# component_models <- components %>%
#   mutate(model_string = paste0(
#     "component_",
#     gsub("-", "_", gsub(",", "", tolower(gsub(" ", "_", response_domain)))),
#     "_model <- 'component_",
#     gsub("-", "_", gsub(",", "", tolower(gsub(" ", "_", gsub(",|and", "", response_domain))))),
#     " =~ ",
#     variables, "'"))
# 
# 
# all_model_strings <- c(
#   subcomponent_models$model_string,
#   component_models$model_string)

# all_model_strings
```

```{r, include=FALSE, echo=FALSE}
# Create the subcomponent and component models for CFA
subcomponent_connectedness_model <- 'subcomponent_connectedness =~ dk + dl'
subcomponent_critical_action_model <- 'subcomponent_critical_action =~ dm'
subcomponent_cultural_identity_and_connection_model <- 'subcomponent_cultural_identity_and_connection =~ dx + dy + dz + ea + eb + ec'
subcomponent_experiences_of_racism_and_discrimination_model <- 'subcomponent_experiences_of_racism_and_discrimination =~ ef + eg + eh + ei + ej + ek + el + em + en'
subcomponent_freedom_to_explore_the_self_model <- 'subcomponent_freedom_to_explore_the_self =~ dd + de + df'
subcomponent_growth_mindset_model <- 'subcomponent_growth_mindset =~ cr + cs'
subcomponent_hope_for_the_future_model <- 'subcomponent_hope_for_the_future =~ co + cp'
subcomponent_microaggressions_model <- 'subcomponent_microaggressions =~ eo + ep + eq + er'
subcomponent_personal_safety_model <- 'subcomponent_personal_safety =~ q19'
subcomponent_positive_emotions_model <- 'subcomponent_positive_emotions =~ ck + cl + cm'
subcomponent_psychological_distress_model <- 'subcomponent_psychological_distress =~ ct + cu + cv + cw + cx + cy'
subcomponent_relationships_support_model <- 'subcomponent_relationships_support =~ q10a + q12a + dn'
subcomponent_safe_access_to_public_spaces <- 'subcomponent_safe_access_to_public_spaces =~ do + dp + dq + dr + ds + dt + du + dv'
subcomponent_self_efficacy_model <- 'subcomponent_self_efficacy =~ cn + cq'
subcomponent_sparks_model <- 'subcomponent_sparks =~ q10'
subcomponent_structural_racism_model <- 'subcomponent_structural_racism =~ es + et + eu + ev + ew + ex + ey'
component_caring_families_and_relationships_model <- 'component_caring_families_and_relationships =~ q10a + q12a + dk + dl + dn'
component_cultural_identity_model <- 'component_cultural_identity =~ dx + dy + dz + ea + eb + ec'
component_positive_identity_and_self_worth_model <- 'component_positive_identity_and_self_worth =~ cn + co + cp + cq + q10 + dd + de + df + dm'
component_racial_justice_equity_and_inclusion_model <- 'component_racial_justice_equity_and_inclusion =~ ef + eg + eh + ei + ej + ek + el + em + en + eo + ep + eq + er + es + et + eu + ev + ew + ex + ey'
component_safety_model <- 'component_safety =~ q19'
component_strong_minds_model <- 'component_strong_minds =~ ck + cl + cm + cr + cs + ct + cu + cv + cw + cx + cy'
component_vibrant_communities_model <- 'component_vibrant_communities =~ do + dp + dq + dr + ds + dt + du + dv'
```

```{r, include=FALSE, echo=FALSE}
# Contains all the component models that have 3 or more question items 
component_models <- c(
  component_caring_families_and_relationships_model,
  component_cultural_identity_model,
  component_positive_identity_and_self_worth_model, 
  component_racial_justice_equity_and_inclusion_model,
  component_strong_minds_model,
  component_vibrant_communities_model
)

# Contains all the subcomponent models that have 3 or more question items 
subcomponent_models <- c(
  subcomponent_experiences_of_racism_and_discrimination_model,
  subcomponent_freedom_to_explore_the_self_model, 
  subcomponent_microaggressions_model,
  subcomponent_positive_emotions_model, 
  subcomponent_psychological_distress_model,
  subcomponent_relationships_support_model, 
  subcomponent_structural_racism_model
)

# Contains all the subcomponent and component models that have less than 3 question items
remaining_models <- c(
  component_safety_model, 
  subcomponent_connectedness_model, 
  subcomponent_critical_action_model, 
  subcomponent_growth_mindset_model, 
  subcomponent_hope_for_the_future_model, 
  subcomponent_personal_safety_model, 
  subcomponent_self_efficacy_model, 
  subcomponent_sparks_model 
  # The model below is exactly the same as component_vibrant_communities_model
  # subcomponent_safe_access_to_public_spaces,  
  # The model below is exactly the same as component_cultural_identity_model
  # subcomponent_cultural_identity_and_connection_model, 
)
```

```{r}
# Run confirmatory factor analysis (CFA) on the models

# Get factor loadings for the components
component_results <- do.call(rbind, lapply(component_models, run_cfa))

# Get factor loadings for the subcomponents
subcomponent_results <- do.call(rbind, lapply(subcomponent_models, run_cfa))

# Get factor loadings for the components and subcomponents with less than 3 items
remaining_results <- do.call(rbind, lapply(remaining_models, run_cfa))
```
<p>Note: subcomponent_safe_access_to_public_spaces is exactly the same as component_vibrant_communities_model. subcomponent_cultural_identity_and_connection_model is exactly the same as component_cultural_identity_model.</p>

```{r}
# This model combines component_positive_identity_and_self_worth_model and 
# component_strong_minds_model into 1 model
positive_identity_and_self_worth_AND_strong_minds_model <- 'positive_identity_and_self_worth_AND_strong_minds_model =~ cn + co + cp + cq + q10 + dd + de + df + dm + ck + cl + cm + cr + cs + ct + cu + cv + cw + cx + cy'

positive_identity_and_self_worth_AND_strong_minds_model_result <- run_cfa(positive_identity_and_self_worth_AND_strong_minds_model)
```

```{r, include=FALSE, echo=FALSE}
# Compile all the model results into a standard data frame
all_results <- as.data.frame(rbind(component_results,subcomponent_results,remaining_results,positive_identity_and_self_worth_AND_strong_minds_model_result))

# Write table with metadata
table_name <- "factor_analysis"
schema <- "youth_thriving"
indicator <- "A table with the results of the factor analysis"
source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Factor Analysis and Correlations/factor_analysis.Rmd "
qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_factor_analysis.docx"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), all_results,
             overwrite = FALSE, row.names = FALSE)

# Comment on table and columns
column_names <- colnames(all_results) # Get column names
column_comments <- c(
  "indicates the component or subcomponent model the factor analysis is being run on",
  "the question that this variable refers to",
  "the subquestion that this variable refers to",
  "the factor loading score of the variable, ranging from 0 to 1",
  "t/f: does the factor loading score of the variable meet the threshold (currently set to 0.6) for what we consider to be a high score (i.e. the variable impacts the component or subcomponent substantially)?",
  "refers to the column label or variable in the survey data",
  "lower bound of the confidence interval for the factor loading score",
  "upper bound of the confidence interval for the factor loading score",
  "standard error of the factor loading score",
  "p-value of the factor loading score",
  "the number of variables in the component or subcomponent that meet the threshold for factor loading scores",
  "the number of variables witin the component or subcomponent",
  "model fit measure: CFI",
  "model fit measure: TLI",
  "model fit measure: RMSEA",
  "model fit measure: SRMR",
  "the question number that this variable refers to",
  "the component this variable belongs to",
  "the category this variable belongs to",
  "the subcomponent this variable belongs to"
)

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)

#dbDisconnect(con)
```

# Step 2: Item Reduction and Component Imputation
<p>Use factor analysis final results to remove items from factor model. Items will be removed starting with items with a load less than 0.6. Factor analysis will then be rerun at different stages of the item reductions until all items in each component are above the threshold as items are reduced. 

Once the final set of items are determined in the model, component scores will be imputed based on the factor model. This will give us an average score for every respondent based on our factor/component model. Select items that do not fit within a factor may be carried forward as separate explanatory variables for the regression (e.g., sparks, safety).</p>

```{r, include=FALSE, echo=FALSE}
# Pull in factor analysis table and filter for survey items that meet the 
# factor score threshold of 0.6
factor_analysis <- dbGetQuery(con, "SELECT * FROM youth_thriving.factor_analysis
                              WHERE met_threshold=true")
```

```{r, include=FALSE, echo=FALSE}
# Create the string names for the subcomponent and component CFA models 

# Group by models and grab each model's variables
 # all_models <- factor_analysis %>%
 #   group_by(model_name) %>%
 #   summarize(variables = paste(variable, collapse = " + "), .groups = "drop")

 # Create model strings for CFA
 # all_models_strings <- all_models %>%
 #   mutate(model_string = paste0(
 #     model_name, "_model",
 #     " <- ",
 #     "'",
 #     model_name,
 #     " =~ '",
 #     variables, "'"))

 # Display all the model strings
 # all_models_strings$model_string
```

```{r, include=FALSE, echo=FALSE}
component_caring_families_and_relationships_model <- 'component_caring_families_and_relationships =~ dl + dk + dn'
component_cultural_identity_model <- 'component_cultural_identity =~ dz + dy + dx + ea + eb + ec'
component_positive_identity_and_self_worth_model <- 'component_positive_identity_and_self_worth =~ co + cp + de + dd + df + cn'
component_racial_justice_equity_and_inclusion_model <- 'component_racial_justice_equity_and_inclusion =~ ek + el + ei + em + en + ej + eh + ef + eg + ep + et + ew + eu + eq + eo + er + es + ev + ey + ex'
component_safety_model <- 'component_safety =~ q19'
component_strong_minds_model <- 'component_strong_minds =~ cy + cu + cw + cv + ct + cx'
component_vibrant_communities_model <- 'component_vibrant_communities =~ dq + du + dp + dr + dv + dt + do + ds'
positive_identity_and_self_worth_AND_strong_minds_model_model <- 'positive_identity_and_self_worth_AND_strong_minds_model =~ cy + cu + co + cp + cw + cn + cm + cr + dd + de'
subcomponent_connectedness_model <- 'subcomponent_connectedness =~ dk + dl'
subcomponent_critical_action_model <- 'subcomponent_critical_action =~ dm'
subcomponent_experiences_of_racism_and_discrimination_model <- 'subcomponent_experiences_of_racism_and_discrimination =~ ek + el + ei + en + em + ej + eh + ef + eg'
subcomponent_freedom_to_explore_the_self_model <- 'subcomponent_freedom_to_explore_the_self =~ de + dd + df'
subcomponent_growth_mindset_model <- 'subcomponent_growth_mindset =~ cr'
subcomponent_hope_for_the_future_model <- 'subcomponent_hope_for_the_future =~ co + cp'
subcomponent_microaggressions_model <- 'subcomponent_microaggressions =~ ep + eq + eo + er'
subcomponent_personal_safety_model <- 'subcomponent_personal_safety =~ q19'
subcomponent_positive_emotions_model <- 'subcomponent_positive_emotions =~ cl + cm + ck'
subcomponent_psychological_distress_model <- 'subcomponent_psychological_distress =~ cy + cu + cw + cv + ct + cx'
subcomponent_relationships_support_model <- 'subcomponent_relationships_support =~ dn + q12a'
subcomponent_self_efficacy_model <- 'subcomponent_self_efficacy =~ cn'
subcomponent_sparks_model <- 'subcomponent_sparks =~ q10'
subcomponent_structural_racism_model <- 'subcomponent_structural_racism =~ et + ew + ey + eu + ev + es + ex'
```

```{r, include=FALSE, echo=FALSE}
# Contains all the component models that have 3 or more question items 
component_models <- c(
  component_caring_families_and_relationships_model,
  component_cultural_identity_model,
  component_positive_identity_and_self_worth_model, 
  component_racial_justice_equity_and_inclusion_model,
  component_strong_minds_model,
  component_vibrant_communities_model
)

# Contains all the subcomponent models that have 3 or more question items 
subcomponent_models <- c(
  subcomponent_experiences_of_racism_and_discrimination_model,
  subcomponent_freedom_to_explore_the_self_model, 
  subcomponent_microaggressions_model,
  subcomponent_positive_emotions_model, 
  subcomponent_psychological_distress_model,
  subcomponent_relationships_support_model, 
  subcomponent_structural_racism_model
)

# Contains all the subcomponent and component models that have less than 3 question items
remaining_models <- c(
  component_safety_model, 
  subcomponent_connectedness_model, 
  subcomponent_critical_action_model, 
  subcomponent_growth_mindset_model, 
  subcomponent_hope_for_the_future_model, 
  subcomponent_personal_safety_model, 
  subcomponent_self_efficacy_model, 
  subcomponent_sparks_model 
)
```

```{r}
# Run confirmatory factor analysis (CFA) on the models

# Get factor loadings for the components
component_results <- do.call(rbind, lapply(component_models, run_cfa))

# Get factor loadings for the subcomponents
subcomponent_results <- do.call(rbind, lapply(subcomponent_models, run_cfa))

# Get factor loadings for the components and subcomponents with less than 3 items
remaining_results <- do.call(rbind, lapply(remaining_models, run_cfa))
```

```{r, include=FALSE, echo=FALSE}
# Compile all the model results into a standard data frame
all_results <- as.data.frame(rbind(component_results,subcomponent_results,remaining_results))

# Write table with metadata
table_name <- "factor_analysis_item_reduction"
schema <- "youth_thriving"
indicator <- "A table with the results of the factor analysis. In this table, factor analysis was only run on survey items that exceeded the factor score threshold of 0.6, based on the scores from table factor_analysis."
source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Factor Analysis and Correlations/factor_analysis.Rmd "
qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_item_reduction_component_imputation.docx"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), all_results,
             overwrite = TRUE, row.names = FALSE)

# Comment on table and columns
column_names <- colnames(all_results) # Get column names
column_comments <- c(
  "indicates the component or subcomponent model the factor analysis is being run on",
  "the question that this variable refers to",
  "the subquestion that this variable refers to",
  "the factor loading score of the variable, ranging from 0 to 1",
  "t/f: does the factor loading score of the variable meet the threshold (currently set to 0.6) for what we consider to be a high score (i.e. the variable impacts the component or subcomponent substantially)?",
  "refers to the column label or variable in the survey data",
  "lower bound of the confidence interval for the factor loading score",
  "upper bound of the confidence interval for the factor loading score",
  "standard error of the factor loading score",
  "p-value of the factor loading score",
  "the number of variables in the component or subcomponent that meet the threshold for factor loading scores",
  "the number of variables witin the component or subcomponent",
  "model fit measure: CFI",
  "model fit measure: TLI",
  "model fit measure: RMSEA",
  "model fit measure: SRMR",
  "the question number that this variable refers to",
  "the component this variable belongs to",
  "the category this variable belongs to",
  "the subcomponent this variable belongs to"
)

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)

#dbDisconnect(con)
```

```{r, include=FALSE, echo=FALSE}
# Create a function to get the predicted factor scores
run_predictions <- function(model_name) {
  # Fit the data to a CFA model
  fit.cat <- cfa(model_name, data=small_svy_data, std.lv = TRUE, ordered = TRUE)

  # Calculate overall factor scores for the model 
  # and attach the scores to the original data
  idx <- lavInspect(fit.cat, "case.idx")
  fscores <- lavPredict(fit.cat)
  # Loop over factors
  for (fs in colnames(fscores)) {small_svy_data[idx, fs] <- fscores[ , fs]}
  
  # The last column contains the predicted factor scores
  return(small_svy_data %>% select(last_col()))
}
```

```{r, include=FALSE, echo=FALSE}
# measurement_models contains the (sub)component models needed for regression
measurement_models <- c(
  # Dependent variables, Y's
  subcomponent_psychological_distress_model, 
  component_positive_identity_and_self_worth_model,  
  # Explanatory variables, X's
  component_caring_families_and_relationships_model,
  component_cultural_identity_model,
  subcomponent_experiences_of_racism_and_discrimination_model,
  subcomponent_microaggressions_model,  
  subcomponent_structural_racism_model,    
  component_vibrant_communities_model
)
```

```{r, include=FALSE, echo=FALSE}
# predicted_results contains the predicted factor scores for each variable we want to use in the regression
predicted_results <- do.call(cbind, lapply(measurement_models, run_predictions))

# This shows the number of NA values for each (sub)component we want to use in the regression
predicted_results %>% summarise_all(~sum(is.na(.)))

# There are only 769 rows with no NA values
sum(complete.cases(predicted_results))

# Checking the min, mean, and max factor scores for each (sub)component
apply(predicted_results, 2, max, na.rm=TRUE)
apply(predicted_results, 2, mean, na.rm=TRUE)
apply(predicted_results, 2, min, na.rm=TRUE)

# Checking the histograms for each (sub)component
mapply(function(data, name) hist(data, main=name, na.rm=TRUE), 
       as.data.frame(predicted_results), 
       colnames(predicted_results))
```
```{r, include=FALSE, echo=FALSE}
# Write table with metadata
table_name <- "factor_analysis_predicted"
schema <- "youth_thriving"
indicator <- "A table with the predicted factor scores of the subcomponents and components to be used for regression."
source <- "Script: W:/Project/OSI/Bold Vision/Youth Thriving Survey/GitHub/AV/boldvision_youththriving/Factor Analysis and Correlations/factor_analysis.Rmd "
qa_filepath <- "See QA doc for details: W:/Project/OSI/Bold Vision/Youth Thriving Survey/Documentation/QA_item_reduction_component_imputation.docx"
table_comment <- paste0(indicator, source)
dbWriteTable(con, c(schema, table_name), predicted_results,
             overwrite = TRUE, row.names = FALSE)

# Comment on table and columns
column_names <- colnames(predicted_results) # Get column names
column_comments <- c(
  "Predicted factor scores for subcomponent psychological distress",
  "Predicted factor scores for component positive identity and self worth",
  "Predicted factor scores for component caring families and relationships",
  "Predicted factor scores for component cultural identity",
  "Predicted factor scores for subcomponent experiences of racism and discrimination",
  "Predicted factor scores for subcomponent microaggressions",
  "Predicted factor scores for subcomponent structural racism",
  "Predicted factor scores for component vibrant communities"
)

add_table_comments(con, schema, table_name, indicator, source, qa_filepath, column_names, column_comments)

#dbDisconnect(con)
```